---
title: "Study 1: Tables"
---

This script generates the tables for Study 1 (A multidimensional examination of vowel-related articulatory deficits in Parkinson’s disease).

# Packages
```{r}
library(tidyverse)

# Making sure there is a Tables folder
dir.create(path = "Study-1/Tables", showWarnings = F)
```

# Loading the Data
```{r}
speakerList <- rio::import(file = "Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(!`Folder 2`:`Sentence Repetition`) %>%
  base::merge(., fileInventories) %>%
  base::merge(., listenerRatings) %>%
  
  # Making sure dxTime is numeric
  dplyr::mutate(dxTime = as.numeric(dxTime)) %>%
  
  # Refactoring Sex
  dplyr::mutate(Sex = factor(Sex, 
                             levels = c(
                               "M",
                               "F"
                               ),
                             labels = c(
                               "Male Speakers",
                               "Female Speakers"
                             ))) %>%
  
  # Severity-surrogate ratings
  dplyr::mutate(Severity = case_when(
    Group == "HC" ~ "",
    Rating_M > 94 ~ "Normal",
    between(Rating_M, 85, 94.99) ~ "Mild",
    between(Rating_M, 70, 84.99) ~ "Moderate",
    between(Rating_M, 45, 69.99) ~ "Severe",
    Rating_M < 45 ~ "Profound"
  )) %>%
  
  # Removing the MoCA Scores - Not all speakers had them
  dplyr::select(!MoCA)
```

## Table 1 - HC Speaker Demo
```{r}
# HC Speakers ----
speakerList %>%
  dplyr::filter(Group == "HC") %>%
  dplyr::select(!DatabaseID) %>%
  dplyr::arrange(StudyID) %>%
  
  # Creating the gt table
  gt::gt(rowname_col = "StudyID",
    groupname_col = "Sex") %>%
  
  # Title
  gt::tab_header(
      title = "Speaker Demographics"
      ) %>%
  
  # Replace missing values with blanks
  gt::sub_missing(
  columns = everything(),
  rows = everything(),
  missing_text = ""
  ) %>%
  
  # Renaming columns
  gt::cols_label(
    dxTime = "Time Since Diagnosis",
    Rating_M = "Intelligibility (%)",
  ) %>%
  
  # Formatting the Intelligibility data
  gt::fmt_number(
  columns = Rating_M,
  decimals = 2,
  ) %>%
  
  # Adding summary rows
  ## Male Speakers
  gt::summary_rows(
    groups = "Male Speakers",
    columns = c(Age, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list(~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  ## Female Speakers
  gt::summary_rows(
    groups = "Female Speakers",
    columns = c(Age, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list(~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  
  # Adding footnote to Intelligibility
  gt::tab_footnote(
    footnote = "The reported intelligibility (%) scores are aggregated from the Visual Analog Scale (VAS) ratings made for conversational speech samples in the current study.",
    locations = gt::cells_column_labels(
      columns = Rating_M
    )
  ) %>%
  
  # Adding footnote to HCM02
  gt::tab_footnote(
    footnote = "The HCM02 speaker, while healthy and intelligible, had a Spanish accent that likely influenced his intelligibility ratings. Further discussion about this speaker and the implications for his intelligibility ratings can be found in the limitations section.",
    locations = gt::cells_body(
      columns = Rating_M,
      rows = StudyID =="HCM02"
    )
  ) %>%
  
  # Adding footnote to HCM04
  gt::tab_footnote(
    footnote = "The HCM04 speaker, presented with a perceptually rough voice quality consistent with healthy aging. This voice quality likely influenced his intelligibility ratings.",
    locations = gt::cells_body(
      columns = Rating_M,
      rows = StudyID =="HCM04"
    )
  ) %>%
  
  # Format groups
  gt::tab_options(row_group.as_column = FALSE) %>%
  
  # Hiding time since diagnosis and severity
  gt::cols_hide(columns = c(dxTime,Severity)) %>%
  
  # Saving the table
  gt::gtsave(filename = "Table 1_SpeakerDemo_HC.html",
             path = "Study-1/Tables")
```

## Table 2 - PD Speaker Demo
```{r}
# PD Speakers ----
speakerList %>%
  dplyr::filter(Group == "PD") %>%
  dplyr::select(!DatabaseID) %>%
  dplyr::arrange(StudyID) %>%
  
  # Creating the gt table
  gt::gt(rowname_col = "StudyID",
    groupname_col = "Sex") %>%
  
  # Title
  gt::tab_header(
      title = "Speaker Demographics"
      ) %>%
  
  # Replace missing values with blanks
  gt::sub_missing(
  columns = everything(),
  rows = everything(),
  missing_text = ""
  ) %>%
  
  # Renaming columns
  gt::cols_label(
    dxTime = "Time Since Diagnosis (Years)",
    Rating_M = "Intelligibility (%)",
  ) %>%
  
  # Formatting the Intelligibility data
  gt::fmt_number(
  columns = Rating_M,
  decimals = 2,
  ) %>%
  
  # Formatting the dxTime data
  gt::fmt_number(
  columns = dxTime,
  decimals = 0,
  ) %>%
  
  # Adding summary rows
  ## Male Speakers
  gt::summary_rows(
    groups = "Male Speakers",
    columns = c(Age, dxTime, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list(~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  ## Female Speakers
  gt::summary_rows(
    groups = "Female Speakers",
    columns = c(Age, dxTime, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list(~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  # Adding footnote to Intelligibility
  gt::tab_footnote(
    footnote = "The reported intelligibility (%) scores are aggregated from the Visual Analog Scale (VAS) ratings made for conversational speech samples in the current study.",
    locations = gt::cells_column_labels(
      columns = Rating_M
    )
  ) %>%
  
  # Adding footnote to Severity
  gt::tab_footnote(
    footnote = "Severity labels were determined based on the intelligibility measures using the surrogate-severity measures outlined in Stipancic et al. (2022). Specifically, intelligibility values > 94% are `Normal`, 85% - 94% are `Mild`, 70% - 84% are `Moderate`, 45% - 69% are `Severe`, and < 45% are `Profound`.",
    locations = gt::cells_column_labels(
      columns = Severity
    )
  ) %>%
  
  # Format groups
  gt::tab_options(row_group.as_column = FALSE) %>%
  
  # Saving the table
  gt::gtsave(filename = "Table 2_SpeakerDemo_PD.html",
             path = "Study-1/Tables")

```

## Table 5 - Reliability
### Intra-Reliability
```{r}
# Loading the full data to obtain ranges for each measure.
fullData_VSA <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
                dplyr::mutate(aVSA = aVSA / 1000) %>%
                dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
                tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData_ai <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
                dplyr::select(DatabaseID:token,
                              acoDistance, kinDistance,
                              F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "Value")  %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData <- rbind(fullData_ai, fullData_VSA)
rm(fullData_ai, fullData_VSA)

# Diphthong
reliability_ai <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv") %>%
    dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "intraRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
                dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "Value"))


# VSA

reliability_vsa <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "intraRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
                dplyr::mutate(aVSA = aVSA / 1000) %>%
                dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
                tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value"))

reliability <- rbind(reliability_ai %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, intraRel),
                     reliability_vsa %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, intraRel))

# Absolute error
absError_ai <- reliability_ai %>%
  dplyr::mutate(absError = abs(Value - intraRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

absError_vsa <- reliability_vsa %>%
  dplyr::mutate(absError = abs(Value - intraRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

intra_absError <- rbind(absError_ai, absError_vsa) %>%
  base::merge(fullData) %>%
  dplyr::mutate(std_absError = M / range)

stats::cor.test(x = reliability$Value,
                y = reliability$intraRel,
                method = "pearson")
```
### Inter-Reliability
```{r}
# Loading the full data to obtain ranges for each measure.
fullData_VSA <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
                dplyr::mutate(aVSA = aVSA / 1000) %>%
                dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
                tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData_ai <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
                dplyr::select(DatabaseID:token,
                              acoDistance, kinDistance,
                              F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "Value")  %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData <- rbind(fullData_ai, fullData_VSA)
rm(fullData_ai, fullData_VSA)

# Diphthong
reliability_ai <- rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv") %>%
    dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "InterRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
                dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, TB_speedMax) %>%
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "Value"))


# VSA

reliability_vsa <- rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "InterRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
                dplyr::mutate(aVSA = aVSA / 1000) %>%
                dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
                tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value"))

reliability <- rbind(reliability_ai %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, InterRel),
                     reliability_vsa %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, InterRel))

# Absolute error
absError_ai <- reliability_ai %>%
  dplyr::mutate(absError = abs(Value - InterRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

absError_vsa <- reliability_vsa %>%
  dplyr::mutate(absError = abs(Value - InterRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

inter_absError <- rbind(absError_ai, absError_vsa) %>%
  base::merge(fullData) %>%
  dplyr::mutate(std_absError = M / range)

stats::cor.test(x = reliability$Value,
                y = reliability$InterRel,
                method = "pearson")
```
### Table
```{r}
tableData <- base::merge(
  inter_absError %>%
    dplyr::select(Measure,M,std_absError) %>%
    dplyr::rename(inter_absError = M,
                  inter_stdAbsError = std_absError),
  intra_absError %>%
    dplyr::select(Measure,M,std_absError) %>%
    dplyr::rename(intra_absError = M,
                  intra_stdAbsError = std_absError),
) %>%
  dplyr::mutate(Measure = factor(Measure,
                                 levels = c(
                                   "aVSA",
                                   "acoDistance",
                                   "F2_Slope",
                                   "kVSA",
                                   "kinDistance",
                                   "TB_speedMax"
                                 ),
                                 labels = c(
                                   "Acoustic VSA (kHz\U00B2)",
                                   "Acoustic Distance (Hz)",
                                   "F2 Slope (Hz/ms)",
                                   "Kinematic VSA (mm\U00B2)",
                                   "Kinematic Distance (mm)",
                                   "Kinematic Speed (mm/s)"                                 
                                 ))) %>%
  arrange(Measure)

reliabilityTable <- tableData %>%
  gt::gt() %>%
  gt::tab_spanner(columns = c("inter_absError",
                              "inter_stdAbsError"),
                  label = "Inter-measurer") %>%
  gt::tab_spanner(columns = c("intra_absError",
                              "intra_stdAbsError"),
                  label = "Intra-measurer") %>%
  gt::cols_label(
    inter_absError = "MAE",
    inter_stdAbsError = "Std. MAE",
    intra_absError = "MAE",
    intra_stdAbsError = "Std. MAE",
  ) %>%
  gt::fmt_number(
    columns = inter_absError:intra_stdAbsError,
    decimals = 2
  ) %>%
  gt::cols_align(
    align = "right",
    columns = "Measure"
  )
reliabilityTable

gt::gtsave(data = reliabilityTable,
           filename = "Tables/Table 5_Reliability.html")

gt::gtsave(data = reliabilityTable,
           filename = "Tables/Table 5_Reliability.docx")
```

## Table 6 - Descriptives Table
```{r}
# Perceptual Measures ----
perceptualMeasures <- rio::import(file = "Data/PreppedData/ListenerData/ListenerRatings_allRatings.csv") %>%
  dplyr::select(!1) %>%
  
  # Selecting only the data we need
  dplyr::select(DatabaseID, Group, Sex, condition, ratingType, Rating)
  
  ## By Sex
  perceptualMeasures_bySex <- perceptualMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, Sex, condition, ratingType) %>%
    dplyr::summarise(
      M = mean(Rating, na.rm = T),
      SD = sd(Rating, na.rm = T),
      ) %>%
    
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group, condition),
      values_from = c(M,SD),
      )
  
  ## All Speakers
  perceptualMeasures_allSpeakers <- perceptualMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, condition, ratingType) %>%
    dplyr::summarise(
      M = mean(Rating, na.rm = T),
      SD = sd(Rating, na.rm = T),
      ) %>%
    
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group, condition),
      values_from = c(M,SD),
      ) %>%
    
    # Add "All Speakers" label to the Sex
    dplyr::mutate(Sex = "All Speakers")
  
  
  perceptualMeasures <- base::rbind(
    perceptualMeasures_allSpeakers,
    perceptualMeasures_bySex,
    deparse.level = 1) %>%
    dplyr::relocate(Sex, .before = ratingType) %>%
    dplyr::rename(Measure = ratingType)
  
  # Removing the unneeded items
  rm(
    perceptualMeasures_allSpeakers,
    perceptualMeasures_bySex)
  
  

# VSA Measures ----
vsaMeasures <- rio::import(file = "Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
    
    # Converting aVSA from Hz to kHz, to make table cleaner
    dplyr::mutate(aVSA = aVSA / 1000) %>%
  
    # Selecting only the data we need
    dplyr::select(DatabaseID:kVSA) %>%
    
    # Formatting for the table
    tidyr::pivot_longer(cols = aVSA:kVSA,
                        names_to = "Measure",
                        values_to = "Value")

  ## By Sex
  vsaMeasures_bySex <- vsaMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, Sex, condition, Measure) %>%
    dplyr::summarise(
      M = mean(Value, na.rm = T),
      SD = sd(Value, na.rm = T),
      ) %>%
    
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group,condition),
      values_from = c(M,SD),
      )
  
  ## All Speakers
  vsaMeasures_allSpeakers <- vsaMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, condition, Measure) %>%
    dplyr::summarise(
      M = mean(Value, na.rm = T),
      SD = sd(Value, na.rm = T),
      ) %>%
    
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group, condition),
      values_from = c(M,SD),
      ) %>%
    
    # Add "All Speakers" label to the Sex
    dplyr::mutate(Sex = "All Speakers")

vsaMeasures <- base::rbind(
  vsaMeasures_allSpeakers,
  vsaMeasures_bySex,
  deparse.level = 1
  ) %>%
  dplyr::relocate(Sex, .before = Measure)

  # Removing the unneeded items
  rm(
    vsaMeasures_allSpeakers,
    vsaMeasures_bySex)

# /ai/ Measures ----
aiMeasures <- rio::import(file = "Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  
  # Selecting only the data we need
  dplyr::select(
    DatabaseID:Group,
    condition,
    acoDistance,
    kinDistance,
    F2_Slope,
    TB_speedMax,
    ) %>%
  
  # Formatting for the table
  tidyr::pivot_longer(cols = acoDistance:TB_speedMax,
                      names_to = "Measure",
                      values_to = "Value")
  
  ## By sex
  aiMeasures_bySex <- aiMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, Sex, condition, Measure) %>%
    dplyr::summarise(
      M = mean(Value, na.rm = T),
      SD = sd(Value, na.rm = T),
    ) %>%
  
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group,condition),
      values_from = c(M,SD),
      )
  
  ## All Speakers
  aiMeasures_allSpeakers <- aiMeasures %>%
    # Summarizing the measures by taking the average across groups
    dplyr::group_by(Group, condition, Measure) %>%
    dplyr::summarise(
      M = mean(Value, na.rm = T),
      SD = sd(Value, na.rm = T),
    ) %>%
  
    # Pivoting the data back to wide for the table
    tidyr::pivot_wider(
      names_from = c(Group, condition),
      values_from = c(M,SD),
      ) %>%
  
    # Add "All Speakers" label to the Sex
    dplyr::mutate(Sex = "All Speakers")
  
  aiMeasures <- base::rbind(
    aiMeasures_allSpeakers,
    aiMeasures_bySex,
    deparse.level = 1
    ) %>%
    dplyr::relocate(Sex, .before = Measure)
  
  
  # Removing the unneeded items
  rm(
    aiMeasures_allSpeakers,
    aiMeasures_bySex)
  
  
# All Measures ----
descriptivesData <- base::rbind(
  perceptualMeasures,
  vsaMeasures,
  aiMeasures,
  deparse.level = 1
) %>%
    dplyr::mutate_at(vars(-c(Sex,Measure)), round, digits = 2) %>%
    dplyr::mutate(Measure = factor(
      Measure,
      levels = c(
        "Int",
        "AP",
        "aVSA",
        "acoDistance",
        "F2_Slope",
        "kVSA",
        "kinDistance",
        "TB_speedMax",
       ),
       labels = c(
         "Intelligibility (VAS)",
         "Articulatory Precision (VAS)",
         "Acoustic VSA (kHz^2)",
         "Acoustic Distance (Hz)",
         "F2 Slope (Hz/ms)",
         "Kinematic VSA (mm^2)",
         "Kinematic Distance (mm)",
         "Kinematic Speed (mm/s)"
         )),
        Sex = factor(Sex,
                             levels = c(
                               "All Speakers",
                               "M",
                               "F"),
                             labels = c(
                               "All Speakers",
                               "Male Speakers",
                               "Female Speakers"))) %>%
    dplyr::arrange(Measure) %>%
    dplyr::select(
      Sex, Measure,
      M_HC_conv, SD_HC_conv, M_PD_conv, SD_PD_conv,
      M_HC_lessClear, SD_HC_lessClear, M_PD_lessClear, SD_PD_lessClear,
      M_HC_moreClear, SD_HC_moreClear, M_PD_moreClear, SD_PD_moreClear,
    )
  
  # Creating the GT table
  descriptivesTable <- descriptivesData %>%
    gt::gt(
      rowname_col = "Measure",
      groupname_col = "Sex") %>%
  # Spanner 1: PD Speakers
  gt::tab_spanner(
    label = "PD",
    level = 1,
    gather = FALSE,
    columns = c(M_PD_conv, SD_PD_conv,
                M_PD_lessClear, SD_PD_lessClear,
                M_PD_moreClear, SD_PD_moreClear)
  ) %>%
  # Spanner 1: HC Speakers
  gt::tab_spanner(
    label = "HC",
    level = 1,
    gather = FALSE,
    columns = c(M_HC_conv, SD_HC_conv,
                M_HC_lessClear, SD_HC_lessClear,
                M_HC_moreClear, SD_HC_moreClear)
  ) %>%
  # Spanner 2: Conversational
  gt::tab_spanner(
    label = "Conversational",
    level = 2,
    gather = TRUE,
    columns = c(M_HC_conv,
                SD_HC_conv,
                M_PD_conv,
                SD_PD_conv)
  ) %>%
  # Spanner 2: Less Clear
  gt::tab_spanner(
    label = "Less Clear",
    level = 2,
    gather = TRUE,
    columns = c(M_HC_lessClear,
                SD_HC_lessClear,
                M_PD_lessClear,
                SD_PD_lessClear)
  ) %>%
  # Spanner 2: More Clear
  gt::tab_spanner(
    label = "More Clear",
    level = 2,
    gather = TRUE,
    columns = c(M_HC_moreClear,
                SD_HC_moreClear,
                M_PD_moreClear,
                SD_PD_moreClear)
  ) %>%
  gt::cols_label(
    M_HC_conv = "M",
    SD_HC_conv = "SD",
    M_PD_conv = "M",
    SD_PD_conv = "SD",
    M_HC_lessClear = "M",
    SD_HC_lessClear = "SD",
    M_PD_lessClear = "M",
    SD_PD_lessClear = "SD",
    M_HC_moreClear = "M",
    SD_HC_moreClear = "SD",
    M_PD_moreClear = "M",
    SD_PD_moreClear = "SD"
  ) %>%
    
    # Align the measure labels to the right
    gt::cols_align(
      align = c("right"),
      columns = Measure
      ) %>%
  gt::tab_options(row_group.as_column = FALSE)
  
  # Save as HTML
  gt::gtsave(
    data = descriptivesTable,
    filename = "Data/Tables/descriptivesTable.html"
    )
  
  # Save as .docx
  gt::gtsave(
    data = descriptivesTable,
    filename = "Study-1/Tables/Table 3_descriptivesTable.html"
    )

    
```
## Table 7 - Measure Variability
```{r}
myPal <- rcartocolor::carto_pal(n = 15, name = "Geyser")
color_HC <- myPal[2] 
color_PD <- myPal[6]
myPal_1 <- myPal[1]
myPal_2 <- myPal[3]
myPal_3 <- myPal[5]

perceptualMeasures <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings_allRatings.csv") %>%
  dplyr::rename(Measure = ratingType,
                Value = Rating) %>%
  dplyr::group_by(condition, Measure, Sex) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   sd = sd(Value, na.rm = T),
                   CV = sd / M * 100) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Domain = "Perceptual")

vsaMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F")),
                aVSA = aVSA/1000) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(condition, Measure, Sex) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   sd = sd(Value, na.rm = T),
                   CV = sd / M * 100) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Domain = case_when(
    Measure == "aVSA" ~ "Acoustic",
    Measure == "kVSA" ~ "Kinematic",
  ))

aiMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F"))) %>%
  tidyr::pivot_longer(cols = c(acoDistance, kinDistance,
                               F2_Slope, TB_speedMax),
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(condition, Measure, Sex) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   sd = sd(Value, na.rm = T),
                   CV = sd / M * 100) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Domain = case_when(
    Measure == "acoDistance" ~ "Acoustic",
    Measure == "F2_Slope" ~ "Acoustic",
    Measure == "kinDistance" ~ "Kinematic",
    Measure == "TB_speedMax" ~ "Kinematic",
  ))

variabilityMeasures <- rbind(perceptualMeasures,
                             aiMeasures,
                             vsaMeasures) %>%
  dplyr::mutate(condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less Clear",
                                     "Conversational",
                                     "More Clear"
                                   )),
                Measure = factor(Measure,
                                 levels = c(
                                   "Int",
                                   "AP",
                                   "aVSA",
                                   "kVSA",
                                   "acoDistance",
                                   "kinDistance",
                                   "F2_Slope",
                                   "TB_speedMax"
                                 ),
                                 labels = c(
                                   "Intelligibility",
                                   "Articulatory Precision",
                                   "Acoustic VSA",
                                   "Kinematic VSA",
                                   "Acoustic Distance",
                                   "Kinematic Distance",
                                   "F2 Slope",
                                   "Kinematic Speed"
                                 )),
                Domain = factor(Domain,
                                levels = c(
                                  "Perceptual",
                                  "Acoustic",
                                  "Kinematic"))) %>%
  arrange(Measure)

variabilityMeasures %>%
  tidyr::pivot_wider(names_from = c(condition, Sex),
                     values_from = CV,
                     id_cols = c(Domain, Measure)) %>%
  
  # Creating the GT table
  gt::gt(
    rowname_col = "Measure",
    groupname_col = "Domain") %>%
  
  # Spanner for female speakers
  gt::tab_spanner(
    label = gt::md("**Female Speakers**"),
    columns = c(`Less Clear_F`,
                Conversational_F,
                `More Clear_F`)
  ) %>%
  
  # Spanner for male speakers
  gt::tab_spanner(
    label = gt::md("**Male Speakers**"),
    columns = c(`Less Clear_M`,
                Conversational_M,
                `More Clear_M`)
  ) %>%
  
  # Adding the color for male speakers
  gt::data_color(
    columns = c(`Less Clear_M`,
                Conversational_M,
                `More Clear_M`),
    direction = "row",
    palette = myPal[8:15],
    na_color = "white"
  ) %>%
  
  # Adding the color for female speakers
  gt::data_color(
    columns = c(`Less Clear_F`,
                Conversational_F,
                `More Clear_F`),
    direction = "row",
    palette = myPal[8:15],
    na_color = "white"
  ) %>%
  
  # Formatting the CV values
  gt::fmt_number(
    columns = everything(),
    decimals = 2
  ) %>%
  
  # Renaming the columns
  gt::cols_label(
    `Less Clear_F` = gt::md("**LC**"),
    Conversational_F = gt::md("**C**"),
    `More Clear_F` = gt::md("**MC**"),
    `Less Clear_M` = gt::md("**LC**"),
    Conversational_M = gt::md("**C**"),
    `More Clear_M` = gt::md("**MC**"),
  ) %>%
  
  # Formatting the alignment of the columns
  gt::cols_align(
    align = "center",
    columns = c(
      `Less Clear_F`,
      Conversational_F,
      `More Clear_F`,
      `Less Clear_M`,
      Conversational_M,
      `More Clear_M`)
  ) %>%
  
  gt::cols_align(
    align = "right",
    columns = c("Measure")
  ) %>%
  
  # Format groups
  gt::tab_options(row_group.as_column = TRUE) %>%
  
  # Exporting the table
  gt::gtsave(filename = "Tables/Table 7_measurementVariability.html")

```

# Supplemental Info
## Emmeans Tables
```{r}
models <- list.files(path = "Models/")
alpha_s1 <- .05/5

k <- 1
while (k <= NROW(models)) {
  targetModel <- readRDS(file = paste0("Models/",models[k]))
  targetMeasure <- paste0(targetModel@call[["formula"]][[2]])
  
  # Compute EMMs for Group and Sex
  emms_group <- emmeans(targetModel, ~ Group | Sex*condition)
  emms_condition <- emmeans(targetModel, ~ condition | Sex*Group)

  # Compare EMMs for Group and Sex
  pairs(emms_group)
  pairs(emms_condition)
  
  # Compare EMMs for Group and Sex
  groupDiff <- summary(pairs(emms_group)) %>%
    dplyr::rename(stat.value = 7) %>%
      dplyr::mutate(
        Measure = targetMeasure,
        sig = ifelse(p.value < alpha_s1, TRUE, FALSE),
        stat = ifelse(df == "Inf",
                      paste0("z="),
                      paste0("t(",round(df, digits = 2),")=")),
        apa = paste0(Sex, ", ",
                     condition, ", ",
                     contrast, ": ",
                     stat, round(stat.value, digits = 2), ", ",
                   ifelse(p.value < .001, "p<.001", paste0("p=",round(p.value, digits = 3)))),
      apa = gsub(pattern = "0[.]", replacement = ".", apa)) %>%
    dplyr::relocate(Measure, .before = contrast)
  
  conditionDiff <- summary(pairs(emms_condition)) %>%
    dplyr::rename(stat.value = 7) %>%
    dplyr::mutate(
      Measure = targetMeasure,
      sig = ifelse(p.value < alpha_s1, TRUE, FALSE),
      stat = ifelse(df == "Inf",
                    paste0("z="),
                    paste0("t(",round(df, digits = 2),")=")),
      apa = paste0(Sex, ", ",
                   Group, ", ",
                   contrast, ": ",
                   stat, round(stat.value, digits = 2), ", ",
                   ifelse(p.value < .001, "p<.001", paste0("p=",round(p.value, digits = 3)))),
      apa = gsub(pattern = "0[.]", replacement = ".", apa)) %>%
    dplyr::relocate(Measure, .before = contrast)
  
  if (k == 1) {
    table_groupDiff <- groupDiff
    table_conditionDiff <- conditionDiff
  } else {
    table_groupDiff <- rbind(table_groupDiff, groupDiff)
    table_conditionDiff <- rbind(table_conditionDiff, conditionDiff)
  }
  
  k <- k + 1
  rm(groupDiff, conditionDiff, targetMeasure, targetModel)
}

table_groupDiff <- table_groupDiff %>%
  dplyr::mutate(apa_parentheses = gsub(apa, pattern = "(", replacement = "[", fixed=TRUE),
                apa_parentheses = gsub(apa_parentheses,pattern = ")", replacement = "]", fixed=TRUE))

table_conditionDiff <- table_conditionDiff %>%
  dplyr::mutate(apa_parentheses = gsub(apa, pattern = "(", replacement = "[", fixed=TRUE),
                apa_parentheses = gsub(apa_parentheses,pattern = ")", replacement = "]", fixed=TRUE))
```

## Table S1 - Group Contrasts
```{r}
table_groupDiff %>%
  dplyr::select(Measure:condition, estimate, SE, stat.value, df, p.value, sig) %>%
  dplyr::select(!contrast) %>%
  dplyr::mutate(p.value = ifelse(p.value < .001,"<.001", round(p.value, digits = 3)),
                p.value = gsub(p.value, pattern = "0[.]", replacement = ".")) %>%
  tidyr::pivot_wider(
    names_from = Sex,
    values_from = c(estimate, SE, stat.value, p.value,df, sig)
  ) %>%
  dplyr::mutate(
    condition = factor(condition,
                       levels = c(
                         "conv",
                         "lessClear",
                         "moreClear"
                       ),
                       labels = c(
                         "Conversational",
                         "Less Clear",
                         "More Clear"
                       )),
    Measure = factor(Measure,
                     levels = c(
                       "Int",
                       "AP",
                       "aVSA",
                       "acoDistance",
                       "F2_Slope",
                       "kVSA",
                       "kinDistance",
                       "TB_speedMax"
                     ),
                     labels = c(
                       "Intelligibility (%)",
                       "Articulatory Precision (%)",
                       "Acoustic VSA (Hz^2)",
                       "Acoustic Distance (Hz)",
                       "F2 Slope (Hz/ms)",
                       "Kinematic VSA (mm^2)",
                       "Kinematic Distance (mm)",
                       "Kinematic Speed (mm/s)"
                     ))) %>%
  arrange(Measure) %>%
  gt::gt(
    rowname_col = "condition",
    groupname_col = "Measure") %>%
  
  # Female Speakers Spanner
  gt::tab_spanner(
    label = "Female Speakers",
    columns = c(estimate_F,
              SE_F,
              stat.value_F,
              df_F,
              p.value_F)
  ) %>%
  
  # Male Speakers Spanner
  gt::tab_spanner(
    label = "Male Speakers",
    columns = c(estimate_M,
              SE_M,
              stat.value_M,
              df_M,
              p.value_M)
  ) %>%
  gt::fmt_number(
    columns = everything(),
    decimals = 2
  ) %>%
  gt::fmt_number(
    columns = c(p.value_M, p.value_F),
    decimals = 3,
  ) %>%
  gt::cols_align(align = "right",
                 columns = c(p.value_M, p.value_F)) %>%
 
  # Conditionally bold M rows
  gt::tab_style(style = list(gt::cell_text(weight = 'bold')), 
            locations = gt::cells_body(columns = c(
              estimate_M,
              SE_M,
              stat.value_M,
              df_M,
              p.value_M),
              rows = sig_M == TRUE)) %>%
  
  # Conditionally bold M rows
  gt::tab_style(style = list(gt::cell_text(weight = 'bold')), 
            locations = gt::cells_body(columns = c(
              estimate_F,
              SE_F,
              stat.value_F,
              df_F,
              p.value_F),
              rows = sig_F == TRUE)) %>%
  
  # Rename Columns
  gt::cols_label(
    estimate_M = "Est",
    SE_M = "SE",
    stat.value_M = "t",
    df_F = "df",
    p.value_M = "p",
    estimate_F = "Est",
    SE_F = "SE",
    stat.value_F = "t",
    df_M = "df",
    p.value_F = "p"
  ) %>%
  gt::cols_hide(columns = c(sig_M,sig_F)) %>%
  gt::tab_options(row_group.as_column = TRUE)  %>%
  gt::gtsave(filename = "Tables/Table S1_Group Contrasts.html")
```

### Condition Contrasts
```{r}
table_conditionDiff %>%
  dplyr::select(Measure:Group, estimate, SE, stat.value, df, p.value, sig) %>%
  dplyr::mutate(p.value = ifelse(p.value < .001,"<.001", round(p.value, digits = 3)),
                p.value = gsub(p.value, pattern = "0[.]", replacement = ".")) %>%
  tidyr::pivot_wider(
    names_from = Sex,
    values_from = c(estimate, SE, stat.value, p.value,df, sig)
  ) %>%
  dplyr::mutate(
    Measure = factor(Measure,
                     levels = c(
                       "Int",
                       "AP",
                       "aVSA",
                       "acoDistance",
                       "F2_Slope",
                       "kVSA",
                       "kinDistance",
                       "TB_speedMax"
                     ),
                     labels = c(
                       "Intelligibility (%)",
                       "Articulatory Precision (%)",
                       "Acoustic VSA (Hz^2)",
                       "Acoustic Distance (Hz)",
                       "F2 Slope (Hz/ms)",
                       "Kinematic VSA (mm^2)",
                       "Kinematic Distance (mm)",
                       "TB Speed (mm/s)"
                     ))) %>%
  arrange(Measure) %>%
  gt::gt(
    rowname_col = "contrast",
    groupname_col = c("Measure")) %>%
  
  # Female Speakers Spanner
  gt::tab_spanner(
    label = "Female Speakers",
    columns = c(estimate_F,
              SE_F,
              stat.value_F,
              df_F,
              p.value_F)
  ) %>%
  
  # Male Speakers Spanner
  gt::tab_spanner(
    label = "Male Speakers",
    columns = c(estimate_M,
              SE_M,
              stat.value_M,
              df_M,
              p.value_M)
  ) %>%
  gt::fmt_number(
    columns = everything(),
    decimals = 2
  ) %>%
  gt::fmt_number(
    columns = c(p.value_M, p.value_F),
    decimals = 3,
  ) %>%
  gt::cols_align(align = "right",
                 columns = c(p.value_M, p.value_F)) %>%
 
  # Conditionally bold M rows
  gt::tab_style(style = list(gt::cell_text(weight = 'bold')), 
            locations = gt::cells_body(columns = c(
              estimate_M,
              SE_M,
              stat.value_M,
              df_M,
              p.value_M),
              rows = sig_M == TRUE)) %>%
  
  # Conditionally bold M rows
  gt::tab_style(style = list(gt::cell_text(weight = 'bold')), 
            locations = gt::cells_body(columns = c(
              estimate_F,
              SE_F,
              stat.value_F,
              df_F,
              p.value_F),
              rows = sig_F == TRUE)) %>%
  
  # Rename Columns
  gt::cols_label(
    estimate_M = "Est",
    SE_M = "SE",
    stat.value_M = "F/Z Ratio",
    df_F = "df",
    p.value_M = "p",
    estimate_F = "Est",
    SE_F = "SE",
    stat.value_F = "F/Z Ratio",
    df_M = "df",
    p.value_F = "p"
  ) %>%
  gt::cols_hide(columns = c(sig_M,sig_F)) %>%
  gt::tab_options(row_group.as_column = TRUE) %>%
  gt::gtsave(filename = "Data/Tables/Supplemental Info_Condition Contrasts.html")
  
```