---
title: "Dissertation - Data Reliability"
---

```{r}
rm(list = ls())
```

# Packages
```{r}
library(tidyverse) # install.packages('tidyverse')
library(sp) # install.packages('sp')
library(ggpubr) # install.packages('ggpubr')
library(openxlsx) # install.packages('openxlsx')
library(plyr) # install.packages('plyr')
library(PraatR) # install.packages('PraatR')
library(beepr) # install.packages('beepr')
library(irr) # install.packages('irr')
source('../Functions/MSL Tools.R')
```


# Intra-measurer Reliability (Within)
## Loading the Data
```{r}
speakers <- rio::import(file = "../Data/PreppedData/Speaker List.csv")
```

## Creating Folders
```{r}
dir.create(path = "../Data/PreppedData/Reliability",
           showWarnings = F)

# Intra
dir.create(path = "Data/PreppedData/Reliability/Intrameasurer Reliability",
           showWarnings = F)
dir.create(path = "Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments",
           showWarnings = F)
dir.create(path = "Data/PreppedData/Reliability/Intrameasurer Reliability/MovementSegments",
           showWarnings = F)
```

## Target Segments
This code block extracts the target acoustic and movement data. It saves the data in the AcousticSegments and MovementSegments in the RawData > SpeakerData folder.

This data is used in the next section to collate all of the data.
```{r}
relFiles <- list.files("../Data/RawData/SpeakerData/Reliability/Intrameasurer Reliability") %>%
  gsub(pattern = ".TextGrid",
       replacement = "")

speakers <- rio::import(file = "../Data/PreppedData/Speaker List.csv") %>%
  dplyr::mutate(DatabaseID = as.factor(DatabaseID),
                Group = as.factor(Group),
                Sex = as.factor(Sex)) %>%
  dplyr::filter(`Sentence Repetition` %in% relFiles)

# Find which files have already been generated
completed <- list.files(path = "../Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments") %>%
  gsub(pattern = "_AcousticSegments.csv",
       replacement = "_sync",
       x = .) %>%
  as.data.frame() %>%
  dplyr::mutate(completed = TRUE) %>%
  dplyr::rename(`Sentence Repetition` = 1)

# Removing the completed speakers from this process
speakers <- speakers %>%
  base::merge(.,completed, all = TRUE) %>%
  dplyr::mutate(completed = ifelse(is.na(completed),FALSE,TRUE)) %>%
  dplyr::filter(completed == FALSE)


fileInventories <- rio::import("/Volumes/Austin/Databases/CoarticData/File Inventories.xlsx")

databasePath <- function(FileName){
  if(is.null(FileName)) {
    return(paste0("/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Databases/Coartic-Database"))
  } else {
    return(paste0("/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Databases/Coartic-Database/", FileName))
  }
}

NC <- 1

while (NC <= NROW(speakers)) {
  # IDing Speaker & Pulling their info from the master File Inventories.xlsx
  speaker <- speakers$DatabaseID[NC]
  speaker_fileInventories <- fileInventories %>%
    dplyr::filter(`Sub #` == speaker)
  sex <- speaker_fileInventories$Sex
  group <- speaker_fileInventories$Group
  
  # IDing TextGrid Files
  if (speaker == "Sub25") {
    sentRepFile <- "Sub25_1_014_sync"
  } else {
    sentRepFile <- speaker_fileInventories$`Sentence Repetition`
  }
  
  textGridFile <- list.files(path = "../Data/RawData/SpeakerData/Reliability/Intrameasurer Reliability",
                             pattern = sentRepFile,
                             ignore.case = TRUE)
  
  # Reading TextGrid
  tg <- rPraat::tg.read(paste0("../Data/RawData/SpeakerData/Reliability/Intrameasurer Reliability/",textGridFile))
  
  condition <- base::cbind(tg[["condition"]][["t1"]],
                tg[["condition"]][["t2"]],
                tg[["condition"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label)) %>%
    dplyr::filter(label != "")
  
  phrase <- base::cbind(tg[["phrase"]][["t1"]],
                tg[["phrase"]][["t2"]],
                tg[["phrase"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label),
                  condition = case_when(
                    onset > condition$onset[condition$label == "conv"] &
                      offset < condition$offset[condition$label == "conv"] ~ "conv",
                    onset > condition$onset[condition$label == "moreclear"] &
                      offset < condition$offset[condition$label == "moreclear"] ~ "moreClear",
                    onset > condition$onset[condition$label == "lessclear"] &
                      offset < condition$offset[condition$label == "lessclear"] ~ "lessClear",
                  )) %>%
    dplyr::filter(label != "") %>%
    dplyr::group_by(condition) %>%
    dplyr::mutate(phraseToken = make.unique(label)) %>%
    dplyr::ungroup() %>%
    dplyr::relocate(condition, .after = phraseToken)
  
  vowel <- base::cbind(tg[["vowel"]][["t1"]],
                tg[["vowel"]][["t2"]],
                tg[["vowel"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(DatabaseID = speaker,
                  Group = group,
                  onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label),
                  condition = case_when(
                    onset > condition$onset[condition$label == "conv"] &
                      offset < condition$offset[condition$label == "conv"] ~ "conv",
                    onset > condition$onset[condition$label == "moreclear"] &
                      offset < condition$offset[condition$label == "moreclear"] ~ "moreClear",
                    onset > condition$onset[condition$label == "lessclear"] &
                      offset < condition$offset[condition$label == "lessclear"] ~ "lessClear",
                  ),
                  condition = as.factor(condition)) %>%
    dplyr::filter(label != "") %>%
    group_by(DatabaseID, condition) %>%
    dplyr::mutate(token = make.unique(label),
                  phrase = NA) %>%
    dplyr::select(DatabaseID,Group,condition,phrase,label,token,onset,offset)
  
  # Assigning Phrase to each vowel
  k <- 1
  while(k <= NROW(vowel)) {
    onset <- vowel$onset[k]
    offset <- vowel$offset[k]
    midpoint <- ((offset - onset)/2) + onset
    targetPhrase <- phrase %>%
      dplyr::filter(midpoint > onset & midpoint < offset) %>%
      pull(phraseToken)
    
    vowel$phrase[k] <- targetPhrase
    
    k <- k + 1
  }
  rm(k)
  
  # Pulling the formant Data
  formantFile <- list.files(path = "../Data/RawData/SpeakerData/FBWFiles",
             pattern = sentRepFile,
             ignore.case = T)
  
  formants <- utils::read.delim(file = paste0("../Data/RawData/SpeakerData/FBWFiles/",formantFile),
                                header = F) %>%
    dplyr::rename(time = 1,
                  F1 = 2,
                  F2 = 3,
                  F3 = 4) %>%
    dplyr::select(time, F1, F2, F3) %>%
    dplyr::mutate(time = time/1000,
                  F1 = F1*1000,
                  F2 = F2*1000,
                  F3 = F3*1000)
  
  # Pulling the movement data
  speakerFolder <- list.files(paste0(databasePath(NULL),"/"),
             pattern = paste0(speaker),
             ignore.case = TRUE)
  decoupledFile <- list.files(paste0(databasePath(speakerFolder),"/Decoupled Movement/"), 
             pattern = gsub(sentRepFile, pattern = "_sync", replacement = ""),
             ignore.case = TRUE)
  
  movement <- rio::import(paste0(paste0(databasePath(speakerFolder),
                                        "/Decoupled Movement/"),
                                 decoupledFile))
  
  
  k <- 1
  while(k <= nrow(vowel)) {
    
    targetAcoustic <- formants %>%
      dplyr::filter(time >= vowel$onset[k]) %>%
      dplyr::filter(time <= vowel$offset[k]) %>%
      dplyr::mutate(DatabaseID = vowel$DatabaseID[k],
                    Group = vowel$Group[k],
                    condition = vowel$condition[k],
                    phrase = vowel$phrase[k],
                    label = vowel$label[k],
                    token = vowel$token[k]) %>%
      dplyr::relocate(DatabaseID:token, .before = time)
    
    targetMovement <- movement %>%
      dplyr::filter(time >= vowel$onset[k]) %>%
      dplyr::filter(time <= vowel$offset[k]) %>%
      dplyr::mutate(DatabaseID = vowel$DatabaseID[k],
                    Group = vowel$Group[k],
                    condition = vowel$condition[k],
                    phrase = vowel$phrase[k],
                    label = vowel$label[k],
                    token = vowel$token[k]) %>%
      dplyr::relocate(DatabaseID:token, .before = time)
    
    if(k == 1) {
      speakerAcoustic <- targetAcoustic
      speakerMovement <- targetMovement
    } else {
      speakerAcoustic <- rbind(speakerAcoustic, targetAcoustic)
      speakerMovement <- rbind(speakerMovement, targetMovement)
    }
    
    rm(targetAcoustic, targetMovement)
    k <- k + 1
  }
  
  # Saving the Acoustic Segments
  dir.create("../Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments",
             showWarnings = F)
  rio::export(x = speakerAcoustic,
              file = paste0("../Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments/",
                            gsub(pattern = "_sync",
                                 replacement = "_AcousticSegments.csv",
                                 x = sentRepFile)))
  
  # Saving the Movement Segments
  dir.create("../Data/PreppedData/Reliability/Intrameasurer Reliability/MovementSegments",
             showWarnings = F)
  rio::export(x = speakerMovement,
              file = paste0("../Data/PreppedData/Reliability/Intrameasurer Reliability/MovementSegments/",
                            gsub(pattern = "_sync",
                                 replacement = "_MovementSegments.csv",
                                 x = sentRepFile)))
  
  NC <- NC + 1
}

print("Done!")

# Alert that the code is finished running
beepr::beep(sound = 3)
```

## Collate Data
This block of code compiles all of the acoustic & movement data.
```{r}
# Creating Compiled Data
dir.create(path = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData",
           showWarnings = F)

# Acoustic Segments
file_names <- paste0("../Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments/",
                     dir(path = "../Data/PreppedData/Reliability/Intrameasurer Reliability/AcousticSegments"))
allAcousticSegments <- base::do.call(rbind,lapply(file_names,read.csv)) %>%
    dplyr::filter(label != "ksent")


rio::export(x = allAcousticSegments,
            file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv")

# Movement Segments
file_names <- paste0("../Data/PreppedData/Reliability/Intrameasurer Reliability/MovementSegments/",
                     dir(path = "../Data/PreppedData/Reliability/Intrameasurer Reliability/MovementSegments"))
allMovementSegments <- base::do.call(rbind,lapply(file_names,read.csv))

rio::export(x = allMovementSegments,
            file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv")
```



## Target Measures

### Temporal midpoint
This script calculates the temporal midpoint for the corner vowels, which will be used to measure acoustic and kinematic VSA in the next section.
```{r}
VowelData_acoustic <- rio::import("../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(label == "a" | label == "i" | label == "ae" | label == "o") %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(acoData = data)

VowelData_kinematic <- rio::import("../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(label == "a" | label == "i" | label == "ae" | label == "o") %>% 
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(ctb_x = scale(tb_x, center = T, scale = F),
                ctb_y = scale(tb_y, center = T, scale = F)) %>%
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(kinData = data)

vowelData_nested <- base::merge(VowelData_acoustic, VowelData_kinematic)


tempMid <- function(data,measure) {

  tempMid_data <- data %>%
    dplyr::mutate(tempMid = (max(time, na.rm = T) - min(time, na.rm = T)) / 2 + min(time, na.rm = T),
                  tempMid_diff = abs(time - tempMid)) %>%
    dplyr::filter(which.min(tempMid_diff) == row_number())

    tempMid_data <- tempMid_data %>%
    pull({{measure}}) %>%
    as.numeric()
    
   return(tempMid_data)

}

# apply the function to each group defined by DatabaseID, condition, and token
vowelData_tempMid <- vowelData_nested %>%
  dplyr::mutate(time_tempMid = map(acoData, tempMid, measure = time),
                F1_tempMid = map(acoData, tempMid, measure = F1),
                F2_tempMid = map(acoData, tempMid, measure = F2),
                F3_tempMid = map(acoData, tempMid, measure = F3),
                TF_x_tempMid = map(kinData, tempMid, measure = tf_x),
                TF_y_tempMid = map(kinData, tempMid, measure = tf_y),
                TB_x_tempMid = map(kinData, tempMid, measure = tb_x),
                TB_y_tempMid = map(kinData, tempMid, measure = tb_y),
                cTB_x_tempMid = map(kinData, tempMid, measure = ctb_x),
                cTB_y_tempMid = map(kinData, tempMid, measure = ctb_y),
                )

rio::export(x = vowelData_tempMid %>%
              dplyr::select(!acoData:kinData),
            file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_tempMid.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)

```

### VSA
This block calculates:
(1) aVSA (acoustic VSA)
(2) kVSA (kinematic VSA)

```{r}
vsa <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_tempMid.csv") %>%
    dplyr::mutate(rep = base::sub(pattern = ".*[.]",
                                     replacement = "",
                                     x = phrase),
                  rep = as.numeric(rep) + 1,
                  rep = case_when(
                    is.na(rep) ~ 1,
                    TRUE ~ rep,
                  ),
                  phrase = base::sub(pattern = "[.].*",
                                     replacement = "",
                                     x = phrase)) %>%
  dplyr::rename(F1 = F1_tempMid,
                F2 = F2_tempMid,
                TB_x = TB_x_tempMid,
                TB_y = TB_y_tempMid,
                cTB_x = cTB_x_tempMid,
                cTB_y = cTB_y_tempMid,
                ) %>%
  dplyr::group_by(DatabaseID,
                  Group,
                  condition,
                  label,
                  ) %>%
  dplyr::summarise(F1 = mean(F1, na.rm = T),
                   F2 = mean(F2, na.rm = T),
                   TB_x = mean(TB_x, na.rm = T),
                   TB_y = mean(TB_y, na.rm = T),
                   cTB_x = mean(cTB_x, na.rm = T),
                   cTB_y = mean(cTB_y, na.rm = T),
                   ) %>%
  dplyr::group_by(
    DatabaseID,
    Group,
    condition,
    ) %>%
  # The cHull function calculates the VSA
  dplyr::summarise(aVSA = cHull(F2, F1),
                   kVSA = cHull(TB_x, TB_y),
                   kVSA_centered = cHull(cTB_x, cTB_y),
                   )


rio::export(x = vsa,
            file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_VSA.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)
  
```
### /ai/ segments
This segment of the script calculates:
  (1) F2 Slope
  (2) acoustic distance
  (3) decoupled TB distance
  (4) coupled TB distance
  (5) jaw distance
  (6) decoupled TB speed
  (7) coupled TB speed
  (8) jaw speed
  
```{r}
source('../Functions/MSL Tools.R')

# Prepping and nesting the data
aiData_acoustic <- rio::import("../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(label == "ai")

aiData_acoustic_nested <- aiData_acoustic %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(acoData = data)

aiData_kinematic <- rio::import("../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(label == "ai")

aiData_kinematic_nested <- aiData_kinematic %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(kinData = data)

aiData_nested <- base::merge(aiData_acoustic_nested,
                             aiData_kinematic_nested)

rm(aiData_acoustic, aiData_acoustic_nested,
   aiData_kinematic, aiData_kinematic_nested)

exampleData <- aiData_nested[[7]][[1]] # conv
exampleData <- aiData_nested[[7]][[6]] #lessClear
data <- aiData_nested[[8]][[1]]

# /ai/ Acoustic Analysis Function
ai_aco <- function(data, measure) {
  
# Acoustic Distance ----
  data <- data %>%
    dplyr::filter(F2 != 0) %>%
    dplyr::mutate(F2_z = abs(scale(F2)),
                  F1_z = abs(scale(F1))) %>%
    # this gets rid of F2 outliers that were missed in smoothing
    dplyr::filter(F2_z < 2) #%>%
    #dplyr::mutate(F1 = ifelse(F1_z >= 2,NA,F1))

# F2 Slope ---
## F1 Cubic
fit1_F1 <- lm(F1 ~ poly(time,1), data = data)
fit1_F1_sum <- summary(fit1_F1)
fit1_F1_r2 <- fit1_F1_sum$r.squared

fit2_F1 <- lm(F1 ~ poly(time,2), data = data)
fit2_F1_sum <- summary(fit2_F1)
fit2_F1_r2 <- fit2_F1_sum$r.squared

fit3_F1 <- lm(F1 ~ poly(time,3), data = data)
fit3_F1_sum <- summary(fit3_F1)
fit3_F1_r2 <- fit3_F1_sum$r.squared

## F2 Cubic
fit1_F2 <- lm(F2 ~ poly(time,1), data = data)
fit1_F2_sum <- summary(fit1_F2)
fit1_F2_r2 <- fit1_F2_sum$r.squared

fit2_F2 <- lm(F2 ~ poly(time,2), data = data)
fit2_F2_sum <- summary(fit2_F2)
fit2_F2_r2 <- fit2_F2_sum$r.squared

fit3_F2 <- lm(F2 ~ poly(time,3), data = data)
fit3_F2_sum <- summary(fit3_F2)
fit3_F2_r2 <- fit3_F2_sum$r.squared

bestFit <- which.max(c(fit1_F2_r2,fit2_F2_r2,fit3_F2_r2))

if (bestFit == 1) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit1_F2, data = .),
                  pred_F1 = predict(fit1_F1, data = .),
                  bestFit = "linear")
} else if (bestFit == 2) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit2_F2, data = .),
                  pred_F1 = predict(fit2_F1, data = .),
                  bestFit = "quadratic")
} else if (bestFit == 3) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit3_F2, data = .),
                  pred_F1 = predict(fit3_F1, data = .),
                  bestFit = "cubic")
}

onset <- data$time[which.min(data$pred_F2)]
offset <- data$time[which.max(data$pred_F2)]

if (onset < offset) {
  ai <- data %>%
    dplyr::filter(F2 > 5) %>%
    dplyr::filter(time > onset) %>%
    dplyr::filter(time < offset)
} else {
  ai <- data %>%
    dplyr::filter(F2 > 5)
}

aiMeasures <- data_frame() %>%
  add_row() %>%
  dplyr::mutate(
    onset = min(ai$time),
    offset = max(ai$time),
    duration = offset - onset,
    highF2_F2 = base::max(ai$F2),
    highF2_F1 = first(ai$F1[ai$F2 == base::max(ai$F2)]),
    lowF2_F2 = base::min(ai$F2),
    lowF2_F1 = first(ai$F1[ai$F2 == base::min(ai$F2)]),
    extent = highF2_F2 - lowF2_F2,
    F2_Slope = extent/(duration*1000),
    bestFit = unique(ai$bestFit))

    aiMeasures <- aiMeasures %>%
    pull({{measure}})
    
   return(aiMeasures)

}

ai_kin <- function(data, measure) {
  
# Kinematic Distance ----
  onsetData <- data %>%
    first()
  
  offsetData <- data %>%
    last()
  
# Speed
  data <- data %>%
    dplyr::mutate(time_diff = diff(c(NA,time)),
                  TB_dist = c(NA,base::sqrt(diff(.$tb_x)^2 + diff(.$tb_y)^2)),
                  TB_speed = TB_dist/time_diff,
                  dTB_dist = c(NA,base::sqrt(diff(.$decoupled_tb_x)^2 + diff(.$decoupled_tb_y)^2)),
                  dTB_speed = dTB_dist/time_diff,
                  Jaw_dist = c(NA,base::sqrt(diff(.$jaw_x)^2 + diff(.$jaw_y)^2)),
                  Jaw_speed = Jaw_dist/time_diff,
                  )
    
  
aiMeasures <- data_frame() %>%
  add_row() %>%
  dplyr::mutate(
    onset = min(data$time),
    offset = max(data$time),
    duration = offset - onset,
    # X and Y for Kinematic Distance
    onset_TB_x = onsetData$tb_x,
    onset_TB_y = onsetData$tb_y,
    offset_TB_x = offsetData$tb_x,
    offset_TB_y = offsetData$tb_y,
    # TB measures
    TB_speedAvg = base::mean(data$TB_speed, na.rm = T),
    TB_speedMax = base::max(data$TB_speed, na.rm = T),
    TB_distance = base::sum(data$TB_dist, na.rm = T),
    TB_displacement = pull(euclideanDistance(x1 = onsetData$tb_x,
                                        y1 = onsetData$tb_y,
                                        x2 = offsetData$tb_x,
                                        y2 = offsetData$tb_y)),
    # dTB measures
    dTB_speedAvg = base::mean(data$dTB_speed, na.rm = T),
    dTB_speedMax = base::max(data$dTB_speed, na.rm = T),
    dTB_distance = base::sum(data$dTB_dist, na.rm = T),
    dTB_displacement = pull(euclideanDistance(x1 = onsetData$decoupled_tb_x,
                                        y1 = onsetData$decoupled_tb_y,
                                        x2 = offsetData$decoupled_tb_x,
                                        y2 = offsetData$decoupled_tb_y)),
    # Jaw measures
    Jaw_speedAvg = base::mean(data$Jaw_speed, na.rm = T),
    Jaw_speedMax = base::max(data$Jaw_speed, na.rm = T),
    Jaw_distance = base::sum(data$Jaw_dist, na.rm = T),
    Jaw_displacement = pull(euclideanDistance(x1 = onsetData$jaw_x,
                                        y1 = onsetData$jaw_y,
                                        x2 = offsetData$jaw_x,
                                        y2 = offsetData$jaw_y)),
    )
    

    aiMeasures <- aiMeasures %>%
    pull({{measure}})
    
   return(aiMeasures)

}

# /ai/ Acoustic Analysis

# apply the function to each group defined by DatabaseID, condition, and token
aiData_Measures_nested <- aiData_nested %>%
  dplyr::mutate(
    # Acoustic Temporal Info
    onset = map(acoData, ai_aco, measure = onset),
    offset = map(acoData, ai_aco, measure = offset),
    duration = map(acoData, ai_aco, measure = duration),
    # F1 and F2 used to measure acoDistance
    highF2_F1 = map(acoData, ai_aco, measure = highF2_F1),
    highF2_F2 = map(acoData, ai_aco, measure = highF2_F2),
    lowF2_F1 = map(acoData, ai_aco, measure = lowF2_F1),
    lowF2_F2 = map(acoData, ai_aco, measure = lowF2_F2),
    # F2 Slope
    extent = map(acoData, ai_aco, measure = extent),
    F2_Slope = map(acoData, ai_aco, measure = F2_Slope),
    bestFit = map(acoData, ai_aco, measure = bestFit)) %>%
  
  # Now filtering the kinData to only include the transition phase
  unnest(kinData) %>%
  group_by(DatabaseID,Group,condition,phrase,label,token, onset, offset, duration, highF2_F1, highF2_F2, lowF2_F1, lowF2_F2, extent, F2_Slope, bestFit, acoData) %>%
  dplyr::filter(time >= onset & time <= offset) %>%
  nest() %>%
  dplyr::rename(kinData = data) %>%

  # Now calculate the kinematic measures
  dplyr:: mutate(
    # X and Y used to measure kinDistance
    onset_TB_x = map(
      kinData,
      ai_kin,
      measure = onset_TB_x
    ),
    onset_TB_y = map(
      kinData,
      ai_kin,
      measure = onset_TB_y
    ),
    offset_TB_x = map(
      kinData,
      ai_kin,
      measure = offset_TB_x
    ),
    offset_TB_y = map(
      kinData,
      ai_kin,
      measure = offset_TB_y
    ),
    # TB Measures
    TB_speedAvg = map(
      kinData,
      ai_kin,
      measure = TB_speedAvg
    ),
    TB_speedMax = map(
      kinData,
      ai_kin,
      measure = TB_speedMax
    ),
    TB_distance = map(
      kinData,
      ai_kin,
      measure = TB_distance
    ),
    TB_displacement = map(
      kinData,
      ai_kin,
      measure = TB_displacement
    ),
    # dTB Measures
    dTB_speedAvg = map(
      kinData,
      ai_kin,
      measure = dTB_speedAvg
    ),
    dTB_speedMax = map(
      kinData,
      ai_kin,
      measure = dTB_speedMax
    ),
    dTB_distance = map(
      kinData,
      ai_kin,
      measure = dTB_distance
    ),
    dTB_displacement = map(
      kinData,
      ai_kin,
      measure = dTB_displacement
    ),
    # Jaw Measures
    Jaw_speedAvg = map(
      kinData,
      ai_kin,
      measure = Jaw_speedAvg
    ),
    Jaw_speedMax = map(
      kinData,
      ai_kin,
      measure = Jaw_speedMax
    ),
    Jaw_distance = map(
      kinData,
      ai_kin,
      measure = Jaw_distance
    ),
    Jaw_displacement = map(
      kinData,
      ai_kin,
      measure = Jaw_displacement
    ),
  )

aiData_Measures <- aiData_Measures_nested %>%
  dplyr::ungroup() %>%
  dplyr::select(!c(acoData, kinData)) %>%
  unnest() %>%
  group_by(DatabaseID,Group,condition,phrase,label,token) %>%
  dplyr::mutate(acoDistance = pull(euclideanDistance(x1 = highF2_F2,
                                                y1 = highF2_F1,
                                                x2 = lowF2_F2,
                                                y2 = lowF2_F1)),
                kinDistance = pull(euclideanDistance(x1 = onset_TB_x,
                                                y1 = onset_TB_y,
                                                x2 = offset_TB_x,
                                                y2 = offset_TB_y)),
                kinSpeed = kinDistance / duration)


rio::export(x = aiData_Measures,
            file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_aiMeasures.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)
```

## Final Measures
This block cleans up the final Target Measures for analysis
```{r}
speakers <- rio::import(file = "../Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(DatabaseID:Age)

listenerRatings <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings.csv") %>%
  dplyr::select(!1) %>%
  tidyr::pivot_wider(id_cols = c(DatabaseID, condition,Sent, rep),
                     names_from = ratingType,
                     values_from = c(M,SD,Count)) %>%
  dplyr::rename(AP_M = M_AP,
                AP_SD = SD_AP,
                AP_N = Count_AP,
                Int_M = M_Int,
                Int_SD = SD_Int,
                Int_N = Count_Int,
                ) %>%
  dplyr::group_by(DatabaseID, condition, rep) %>%
  dplyr::summarise(Int_M = mean(Int_M, na.rm = T),
                   Int_N = sum(Int_N),
                   AP_M = mean(AP_M, na.rm = T),
                   AP_N = sum(AP_N),
                   )
  
# /ai/ measures
aiMeasures <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_aiMeasures.csv") %>%
  dplyr::select(DatabaseID:duration,
                acoDistance,
                kinDistance,
                F2_Slope,
                TB_speedAvg,
                TB_speedMax,
                TB_distance,
                dTB_speedAvg,
                dTB_speedMax,
                dTB_distance,
                Jaw_speedAvg,
                Jaw_speedMax,
                ) %>%
  base::merge(., speakers) %>%
  dplyr::mutate(rep = base::sub(pattern = ".*[.]",
                                     replacement = "",
                                     x = phrase),
                  rep = as.numeric(rep) + 1,
                  rep = case_when(
                    is.na(rep) ~ 1,
                    TRUE ~ rep,
                  )) %>%
  dplyr::relocate(StudyID:Age, .after = DatabaseID) %>%
  base::merge(., listenerRatings, all = T) %>%
  dplyr::relocate(rep, .after = phrase) %>%
  dplyr::relocate(condition, .after = Group) %>%
  
  # Removing instances of "-Inf" and replacing it with NA
  dplyr::mutate(
    TB_speedMax = ifelse(TB_speedMax == "-Inf",NA,TB_speedMax),
    dTB_speedMax = ifelse(dTB_speedMax == "-Inf",NA,dTB_speedMax),
    TB_distance = ifelse(TB_distance == 0,NA,TB_distance),
    dTB_distance = ifelse(dTB_distance == 0,NA,dTB_distance),
    ) %>%
  
  # Removing an outlier for TB_speedMax
  dplyr::mutate(TB_speedMax = ifelse(TB_speedMax > 600,NA,TB_speedMax)) %>%
  
  # Removing instances of empty rows
  dplyr::filter(!is.na(onset))

  rio::export(x = aiMeasures, file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv")
  
# VSA Measures ----
  vsaMeasures <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/allSpeakers_VSA.csv") %>%
    base::merge(., speakers) %>%
    base::merge(., listenerRatings %>%
                  dplyr::group_by(DatabaseID,condition) %>%
                  dplyr::summarise(
                    Int_M = base::mean(Int_M, na.rm = T),
                    Int_N = base::sum(Int_N, na.rm = T),
                    AP_M = base::mean(AP_M, na.rm = T),
                    AP_N = base::sum(AP_N, na.rm = T),
                    )) %>%
    dplyr::select(DatabaseID, StudyID, Group, Sex, Age, condition, aVSA:kVSA,Int_M:AP_N)
  
  rio::export(x = vsaMeasures, file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv")
```

## Calculating Intra-Reliability
```{r}
# Loading the full data to obtain ranges for each measure.
fullData_VSA <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA, kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData_ai <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(kinSpeed = kinDistance / (duration * 1000)) %>%
  dplyr::select(DatabaseID:token,
                acoDistance,
                kinDistance,
                F2_Slope,
                kinSpeed) %>%
  tidyr::pivot_longer(
    cols = acoDistance:kinSpeed,
    names_to = "Measure",
    values_to = "Value"
  )  %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData <- rbind(fullData_ai, fullData_VSA)
rm(fullData_ai, fullData_VSA)

# Diphthong
reliability_ai <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv") %>%
    dplyr::mutate(kinSpeed = kinDistance / (duration * 1000)) %>%
    dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, kinSpeed) %>%
  tidyr::pivot_longer(cols = acoDistance:kinSpeed,
                      names_to = "Measure",
                      values_to = "intraRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
                dplyr::mutate(kinSpeed = kinDistance / (duration * 1000)) %>%
                dplyr::select(DatabaseID:token, acoDistance, kinDistance, F2_Slope, kinSpeed) %>%
  tidyr::pivot_longer(cols = acoDistance:kinSpeed,
                      names_to = "Measure",
                      values_to = "Value"))


# VSA

reliability_vsa <- rio::import(file = "../Data/PreppedData/Reliability/Intrameasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "intraRel") %>%
  base::merge(.,
              rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
                dplyr::mutate(aVSA = aVSA / 1000) %>%
                dplyr::select(DatabaseID:condition, aVSA,kVSA) %>%
                tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value"))

reliability <- rbind(reliability_ai %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, intraRel),
                     reliability_vsa %>%
                       dplyr::select(DatabaseID, StudyID, Group, Age, condition, Measure, Value, intraRel))

# Calculating ICC
my_icc <- function(data) {
  data %>%
    select(Value, intraRel) %>% # select just the rating columns
    irr::icc(model = "twoway",
             type = "agreement",
             unit = "single") %>%        # calculate the ICC
    unlist() %>%          # turn the output list into a vector
    t() %>%               # transpose this vector
    as_tibble() %>%       # turn the vector into a table 
    select(               # select just the columns you want
      stimuli = subjects, # rename subjects to stimuli     
      raters, 
      icc = value,        # rename value to icc
      lbound, 
      ubound
    ) %>%
    # fix column modes (unlisting turned them all into characters)
    mutate_at(vars(stimuli, raters), as.integer) %>% 
    mutate_at(vars(icc:ubound), as.numeric)
}

ICC_intra <- reliability %>%
  dplyr::select(Measure, Value, intraRel) %>%
  dplyr::group_by(Measure) %>%
  nest() %>%                                       # nest the rest of the columns
  mutate(icc = map(data, my_icc)) %>%              # calculate ICC for each group
  unnest(icc) %>%                                  # expand the tables returned to icc
  select(-data) %>%
  dplyr::mutate(
    intra_ICC = round(icc, digits = 2),
    intra_lbound = round(lbound, digits = 2),
    intra_ubound = round(ubound, digits = 2),
    APA = paste0(
    Measure, ", ICC(2,A) = ",
    intra_ICC, ", 95% CI [",
    intra_lbound, " - ",
    intra_ubound, "]"
  ))


# Absolute error
absError_ai <- reliability_ai %>%
  dplyr::mutate(absError = abs(Value - intraRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

absError_vsa <- reliability_vsa %>%
  dplyr::mutate(absError = abs(Value - intraRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

intra_absError <- rbind(absError_ai, absError_vsa) %>%
  base::merge(fullData) %>%
  dplyr::mutate(std_absError = M / range)

stats::cor.test(x = reliability$Value,
                y = reliability$intraRel,
                method = "pearson")
```


# Inter-measurer Reliability (Within)
## Loading the Data
```{r}
speakers <- rio::import(file = "../Data/PreppedData/Speaker List.csv")
```

## Creating Folders
```{r}
dir.create(path = "../Data/PreppedData/Reliability",
           showWarnings = F)
# Inter
dir.create(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability",
           showWarnings = F)
dir.create(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments",
           showWarnings = F)
dir.create(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/MovementSegments",
           showWarnings = F)
```

## Target Segments
This code block extracts the target acoustic and movement data. It saves the data in the AcousticSegments and MovementSegments in the RawData > SpeakerData folder.

This data is used in the next section to collate all of the data.
```{r}
relFiles <- list.files("../Data/RawData/SpeakerData/Reliability/Intermeasurer Reliability") %>%
  gsub(pattern = ".TextGrid",
       replacement = "") %>%
  gsub(pattern = "_CW",
     replacement = "")

speakers <- rio::import(file = "../Data/PreppedData/Speaker List.csv") %>%
  dplyr::mutate(DatabaseID = as.factor(DatabaseID),
                Group = as.factor(Group),
                Sex = as.factor(Sex)) %>%
  dplyr::filter(`Sentence Repetition` %in% relFiles)

# Find which files have already been generated
completed <- list.files(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments") %>%
  gsub(pattern = "_AcousticSegments.csv",
       replacement = "_sync",
       x = .) %>%
    gsub(pattern = "_CW",
     replacement = "") %>%
  as.data.frame() %>%
  dplyr::mutate(completed = TRUE) %>%
  dplyr::rename(`Sentence Repetition` = 1)

# Removing the completed speakers from this process
speakers <- speakers %>%
  base::merge(.,completed, all = TRUE) %>%
  dplyr::mutate(completed = ifelse(is.na(completed),FALSE,TRUE)) %>%
  dplyr::filter(completed == FALSE)


fileInventories <- rio::import("/Volumes/Austin/Databases/CoarticData/File Inventories.xlsx")

databasePath <- function(FileName){
  if(is.null(FileName)) {
    return(paste0("/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Databases/Coartic-Database"))
  } else {
    return(paste0("/Users/austinthompson/Library/CloudStorage/Dropbox/Work/Research/Databases/Coartic-Database/", FileName))
  }
}

NC <- 1

while (NC <= NROW(speakers)) {
  # IDing Speaker & Pulling their info from the master File Inventories.xlsx
  speaker <- speakers$DatabaseID[NC]
  speaker_fileInventories <- fileInventories %>%
    dplyr::filter(`Sub #` == speaker)
  sex <- speaker_fileInventories$Sex
  group <- speaker_fileInventories$Group
  
  # IDing TextGrid Files
  if (speaker == "Sub25") {
    sentRepFile <- "Sub25_1_014_sync"
  } else {
    sentRepFile <- speaker_fileInventories$`Sentence Repetition`
  }
  
  textGridFile <- list.files(path = "../Data/RawData/SpeakerData/Reliability/Intermeasurer Reliability",
                             pattern = sentRepFile,
                             ignore.case = TRUE)
  
  # Reading TextGrid
  tg <- rPraat::tg.read(paste0("../Data/RawData/SpeakerData/Reliability/Intermeasurer Reliability/",textGridFile))
  
  condition <- base::cbind(tg[["condition"]][["t1"]],
                tg[["condition"]][["t2"]],
                tg[["condition"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label)) %>%
    dplyr::filter(label != "")
  
  phrase <- base::cbind(tg[["phrase"]][["t1"]],
                tg[["phrase"]][["t2"]],
                tg[["phrase"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label),
                  condition = case_when(
                    onset > condition$onset[condition$label == "conv"] &
                      offset < condition$offset[condition$label == "conv"] ~ "conv",
                    onset > condition$onset[condition$label == "moreclear"] &
                      offset < condition$offset[condition$label == "moreclear"] ~ "moreClear",
                    onset > condition$onset[condition$label == "lessclear"] &
                      offset < condition$offset[condition$label == "lessclear"] ~ "lessClear",
                  )) %>%
    dplyr::filter(label != "") %>%
    dplyr::group_by(condition) %>%
    dplyr::mutate(phraseToken = make.unique(label)) %>%
    dplyr::ungroup() %>%
    dplyr::relocate(condition, .after = phraseToken)
  
  vowel <- base::cbind(tg[["vowel"]][["t1"]],
                tg[["vowel"]][["t2"]],
                tg[["vowel"]][["label"]]) %>%
    as.data.frame() %>%
    dplyr::rename(onset = 1,
                  offset = 2,
                  label = 3) %>%
    dplyr::mutate(DatabaseID = speaker,
                  Group = group,
                  onset = base::as.numeric(onset),
                  offset = base::as.numeric(offset),
                  label = base::gsub(pattern = " ",
                               replacement = "",
                               x = label),
                  label = base::tolower(label),
                  condition = case_when(
                    onset > condition$onset[condition$label == "conv"] &
                      offset < condition$offset[condition$label == "conv"] ~ "conv",
                    onset > condition$onset[condition$label == "moreclear"] &
                      offset < condition$offset[condition$label == "moreclear"] ~ "moreClear",
                    onset > condition$onset[condition$label == "lessclear"] &
                      offset < condition$offset[condition$label == "lessclear"] ~ "lessClear",
                  ),
                  condition = as.factor(condition)) %>%
    dplyr::filter(label != "") %>%
    group_by(DatabaseID, condition) %>%
    dplyr::mutate(token = make.unique(label),
                  phrase = NA) %>%
    dplyr::select(DatabaseID,Group,condition,phrase,label,token,onset,offset)
  
  # Assigning Phrase to each vowel
  k <- 1
  while(k <= NROW(vowel)) {
    onset <- vowel$onset[k]
    offset <- vowel$offset[k]
    midpoint <- ((offset - onset)/2) + onset
    targetPhrase <- phrase %>%
      dplyr::filter(midpoint > onset & midpoint < offset) %>%
      pull(phraseToken)
    
    if (identical(targetPhrase, character(0))) {
      targetPhrase <- phrase %>%
        dplyr::mutate(endDiff = abs(offset - midpoint),
                      begDiff = abs(onset - midpoint)) %>%
        dplyr::filter(row_number() == which.min(endDiff) |
                        row_number() == which.min(begDiff)) %>%
        tidyr::pivot_longer(
          cols = c(endDiff, begDiff),
          names_to = "time") %>%
        dplyr::filter(row_number() == which.min(value)) %>%
        pull(phraseToken)
    }
    
    vowel$phrase[k] <- targetPhrase
    
    k <- k + 1
  }
  rm(k)
  
  # Pulling the formant Data
  formantFile <- list.files(path = "../Data/RawData/SpeakerData/FBWFiles",
             pattern = sentRepFile,
             ignore.case = T)
  
  formants <- utils::read.delim(file = paste0("../Data/RawData/SpeakerData/FBWFiles/",formantFile),
                                header = F) %>%
    dplyr::rename(time = 1,
                  F1 = 2,
                  F2 = 3,
                  F3 = 4) %>%
    dplyr::select(time, F1, F2, F3) %>%
    dplyr::mutate(time = time/1000,
                  F1 = F1*1000,
                  F2 = F2*1000,
                  F3 = F3*1000)
  
  # Pulling the movement data
  speakerFolder <- list.files(paste0(databasePath(NULL),"/"),
             pattern = paste0(speaker),
             ignore.case = TRUE)
  decoupledFile <- list.files(paste0(databasePath(speakerFolder),"/Decoupled Movement/"), 
             pattern = gsub(sentRepFile, pattern = "_sync", replacement = ""),
             ignore.case = TRUE)
  
  movement <- rio::import(paste0(paste0(databasePath(speakerFolder),
                                        "/Decoupled Movement/"),
                                 decoupledFile))
  
  
  k <- 1
  while(k <= nrow(vowel)) {
    
    targetAcoustic <- formants %>%
      dplyr::filter(time >= vowel$onset[k]) %>%
      dplyr::filter(time <= vowel$offset[k]) %>%
      dplyr::mutate(DatabaseID = vowel$DatabaseID[k],
                    Group = vowel$Group[k],
                    condition = vowel$condition[k],
                    phrase = vowel$phrase[k],
                    label = vowel$label[k],
                    token = vowel$token[k]) %>%
      dplyr::relocate(DatabaseID:token, .before = time)
    
    targetMovement <- movement %>%
      dplyr::filter(time >= vowel$onset[k]) %>%
      dplyr::filter(time <= vowel$offset[k]) %>%
      dplyr::mutate(DatabaseID = vowel$DatabaseID[k],
                    Group = vowel$Group[k],
                    condition = vowel$condition[k],
                    phrase = vowel$phrase[k],
                    label = vowel$label[k],
                    token = vowel$token[k]) %>%
      dplyr::relocate(DatabaseID:token, .before = time)
    
    if(k == 1) {
      speakerAcoustic <- targetAcoustic
      speakerMovement <- targetMovement
    } else {
      speakerAcoustic <- rbind(speakerAcoustic, targetAcoustic)
      speakerMovement <- rbind(speakerMovement, targetMovement)
    }
    
    rm(targetAcoustic, targetMovement)
    k <- k + 1
  }
  
  # Saving the Acoustic Segments
  dir.create("../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments",
             showWarnings = F)
  rio::export(x = speakerAcoustic,
              file = paste0("../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments/",
                            gsub(pattern = "_sync",
                                 replacement = "_AcousticSegments.csv",
                                 x = sentRepFile)))
  
  # Saving the Movement Segments
  dir.create("../Data/PreppedData/Reliability/Intermeasurer Reliability/MovementSegments",
             showWarnings = F)
  rio::export(x = speakerMovement,
              file = paste0("../Data/PreppedData/Reliability/Intermeasurer Reliability/MovementSegments/",
                            gsub(pattern = "_sync",
                                 replacement = "_MovementSegments.csv",
                                 x = sentRepFile)))
  
  NC <- NC + 1
}

print("Done!")

# Alert that the code is finished running
beepr::beep(sound = 3)
```

## Collate Data
This block of code compiles all of the acoustic & movement data.
```{r}
# Creating Compiled Data
dir.create(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData",
           showWarnings = F)

# Acoustic Segments
file_names <- paste0("../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments/",
                     dir(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/AcousticSegments"))
allAcousticSegments <- base::do.call(rbind,lapply(file_names,read.csv)) %>%
    dplyr::filter(label != "ksent")


rio::export(x = allAcousticSegments,
            file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv")

# Movement Segments
file_names <- paste0("../Data/PreppedData/Reliability/Intermeasurer Reliability/MovementSegments/",
                     dir(path = "../Data/PreppedData/Reliability/Intermeasurer Reliability/MovementSegments"))
allMovementSegments <- base::do.call(rbind,lapply(file_names,read.csv))

rio::export(x = allMovementSegments,
            file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv")
```



## Target Measures

## Temporal midpoint
This script calculates the temporal midpoint for the corner vowels, which will be used to measure acoustic and kinematic VSA in the next section.
```{r}
VowelData_acoustic <- rio::import("../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(label == "a" | label == "i" | label == "ae" | label == "o") %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(acoData = data)

VowelData_kinematic <- rio::import("../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(label == "a" | label == "i" | label == "ae" | label == "o") %>% 
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(ctb_x = scale(tb_x, center = T, scale = F),
                ctb_y = scale(tb_y, center = T, scale = F)) %>%
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(kinData = data)

vowelData_nested <- base::merge(VowelData_acoustic, VowelData_kinematic)


tempMid <- function(data,measure) {

  tempMid_data <- data %>%
    dplyr::mutate(tempMid = (max(time, na.rm = T) - min(time, na.rm = T)) / 2 + min(time, na.rm = T),
                  tempMid_diff = abs(time - tempMid)) %>%
    dplyr::filter(which.min(tempMid_diff) == row_number())

    tempMid_data <- tempMid_data %>%
    pull({{measure}}) %>%
    as.numeric()
    
   return(tempMid_data)

}

# apply the function to each group defined by DatabaseID, condition, and token
vowelData_tempMid <- vowelData_nested %>%
  dplyr::mutate(time_tempMid = map(acoData, tempMid, measure = time),
                F1_tempMid = map(acoData, tempMid, measure = F1),
                F2_tempMid = map(acoData, tempMid, measure = F2),
                F3_tempMid = map(acoData, tempMid, measure = F3),
                TF_x_tempMid = map(kinData, tempMid, measure = tf_x),
                TF_y_tempMid = map(kinData, tempMid, measure = tf_y),
                TB_x_tempMid = map(kinData, tempMid, measure = tb_x),
                TB_y_tempMid = map(kinData, tempMid, measure = tb_y),
                cTB_x_tempMid = map(kinData, tempMid, measure = ctb_x),
                cTB_y_tempMid = map(kinData, tempMid, measure = ctb_y),
                )

rio::export(x = vowelData_tempMid %>%
              dplyr::select(!acoData:kinData),
            file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_tempMid.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)

```

## VSA
This block calculates:
(1) aVSA (acoustic VSA)
(2) kVSA (kinematic VSA)

```{r}
vsa <- rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_tempMid.csv") %>%
    dplyr::mutate(rep = base::sub(pattern = ".*[.]",
                                     replacement = "",
                                     x = phrase),
                  rep = as.numeric(rep) + 1,
                  rep = case_when(
                    is.na(rep) ~ 1,
                    TRUE ~ rep,
                  ),
                  phrase = base::sub(pattern = "[.].*",
                                     replacement = "",
                                     x = phrase)) %>%
  dplyr::rename(F1 = F1_tempMid,
                F2 = F2_tempMid,
                TB_x = TB_x_tempMid,
                TB_y = TB_y_tempMid,
                cTB_x = cTB_x_tempMid,
                cTB_y = cTB_y_tempMid,
                ) %>%
  dplyr::group_by(DatabaseID,
                  Group,
                  condition,
                  label,
                  ) %>%
  dplyr::summarise(F1 = mean(F1, na.rm = T),
                   F2 = mean(F2, na.rm = T),
                   TB_x = mean(TB_x, na.rm = T),
                   TB_y = mean(TB_y, na.rm = T),
                   cTB_x = mean(cTB_x, na.rm = T),
                   cTB_y = mean(cTB_y, na.rm = T),
                   ) %>%
  dplyr::group_by(
    DatabaseID,
    Group,
    condition,
    ) %>%
  # The cHull function calculates the VSA
  dplyr::summarise(aVSA = cHull(F2, F1),
                   kVSA = cHull(TB_x, TB_y),
                   kVSA_centered = cHull(cTB_x, cTB_y),
                   )


rio::export(x = vsa,
            file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_VSA.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)
  
```

## /ai/ segments
This segment of the script calculates:
  (1) F2 Slope
  (2) acoustic distance
  (3) decoupled TB distance
  (4) coupled TB distance
  (5) jaw distance
  (6) decoupled TB speed
  (7) coupled TB speed
  (8) jaw speed
  
```{r}
source('../Functions/MSL Tools.R')

# Prepping and nesting the data
aiData_acoustic <- rio::import("../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(label == "ai")

aiData_acoustic_nested <- aiData_acoustic %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(acoData = data)

aiData_kinematic <- rio::import("../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(label == "ai")

aiData_kinematic_nested <- aiData_kinematic %>% 
  group_by(DatabaseID,Group,condition,phrase,label,token) %>% 
  nest() %>%
  dplyr::rename(kinData = data)

aiData_nested <- base::merge(aiData_acoustic_nested,
                             aiData_kinematic_nested)

rm(aiData_acoustic, aiData_acoustic_nested,
   aiData_kinematic, aiData_kinematic_nested)

exampleData <- aiData_nested[[7]][[1]] # conv
exampleData <- aiData_nested[[7]][[6]] #lessClear
data <- aiData_nested[[8]][[1]]

# /ai/ Acoustic Analysis Function
ai_aco <- function(data, measure) {
  
# Acoustic Distance ----
  data <- data %>%
    dplyr::filter(F2 != 0) %>%
    dplyr::mutate(F2_z = abs(scale(F2)),
                  F1_z = abs(scale(F1))) %>%
    # this gets rid of F2 outliers that were missed in smoothing
    dplyr::filter(F2_z < 2) #%>%
    #dplyr::mutate(F1 = ifelse(F1_z >= 2,NA,F1))

# F2 Slope ---
## F1 Cubic
fit1_F1 <- lm(F1 ~ poly(time,1), data = data)
fit1_F1_sum <- summary(fit1_F1)
fit1_F1_r2 <- fit1_F1_sum$r.squared

fit2_F1 <- lm(F1 ~ poly(time,2), data = data)
fit2_F1_sum <- summary(fit2_F1)
fit2_F1_r2 <- fit2_F1_sum$r.squared

fit3_F1 <- lm(F1 ~ poly(time,3), data = data)
fit3_F1_sum <- summary(fit3_F1)
fit3_F1_r2 <- fit3_F1_sum$r.squared

## F2 Cubic
fit1_F2 <- lm(F2 ~ poly(time,1), data = data)
fit1_F2_sum <- summary(fit1_F2)
fit1_F2_r2 <- fit1_F2_sum$r.squared

fit2_F2 <- lm(F2 ~ poly(time,2), data = data)
fit2_F2_sum <- summary(fit2_F2)
fit2_F2_r2 <- fit2_F2_sum$r.squared

fit3_F2 <- lm(F2 ~ poly(time,3), data = data)
fit3_F2_sum <- summary(fit3_F2)
fit3_F2_r2 <- fit3_F2_sum$r.squared

bestFit <- which.max(c(fit1_F2_r2,fit2_F2_r2,fit3_F2_r2))

if (bestFit == 1) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit1_F2, data = .),
                  pred_F1 = predict(fit1_F1, data = .),
                  bestFit = "linear")
} else if (bestFit == 2) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit2_F2, data = .),
                  pred_F1 = predict(fit2_F1, data = .),
                  bestFit = "quadratic")
} else if (bestFit == 3) {
  data <- data %>%
    dplyr::mutate(pred_F2 = predict(fit3_F2, data = .),
                  pred_F1 = predict(fit3_F1, data = .),
                  bestFit = "cubic")
}

onset <- data$time[which.min(data$pred_F2)]
offset <- data$time[which.max(data$pred_F2)]

if (onset < offset) {
  ai <- data %>%
    dplyr::filter(F2 > 5) %>%
    dplyr::filter(time > onset) %>%
    dplyr::filter(time < offset)
} else {
  ai <- data %>%
    dplyr::filter(F2 > 5)
}

aiMeasures <- data_frame() %>%
  add_row() %>%
  dplyr::mutate(
    onset = min(ai$time),
    offset = max(ai$time),
    duration = offset - onset,
    highF2_F2 = base::max(ai$F2),
    highF2_F1 = first(ai$F1[ai$F2 == base::max(ai$F2)]),
    lowF2_F2 = base::min(ai$F2),
    lowF2_F1 = first(ai$F1[ai$F2 == base::min(ai$F2)]),
    extent = highF2_F2 - lowF2_F2,
    F2_Slope = extent/(duration*1000),
    bestFit = unique(ai$bestFit))

    aiMeasures <- aiMeasures %>%
    pull({{measure}})
    
   return(aiMeasures)

}

ai_kin <- function(data, measure) {
  
# Kinematic Distance ----
  onsetData <- data %>%
    first()
  
  offsetData <- data %>%
    last()
  
# Speed
  data <- data %>%
    dplyr::mutate(time_diff = diff(c(NA,time)),
                  TB_dist = c(NA,base::sqrt(diff(.$tb_x)^2 + diff(.$tb_y)^2)),
                  TB_speed = TB_dist/time_diff,
                  dTB_dist = c(NA,base::sqrt(diff(.$decoupled_tb_x)^2 + diff(.$decoupled_tb_y)^2)),
                  dTB_speed = dTB_dist/time_diff,
                  Jaw_dist = c(NA,base::sqrt(diff(.$jaw_x)^2 + diff(.$jaw_y)^2)),
                  Jaw_speed = Jaw_dist/time_diff,
                  )
    
  
aiMeasures <- data_frame() %>%
  add_row() %>%
  dplyr::mutate(
    onset = min(data$time),
    offset = max(data$time),
    duration = offset - onset,
    # X and Y for Kinematic Distance
    onset_TB_x = onsetData$tb_x,
    onset_TB_y = onsetData$tb_y,
    offset_TB_x = offsetData$tb_x,
    offset_TB_y = offsetData$tb_y,
    # TB measures
    TB_speedAvg = base::mean(data$TB_speed, na.rm = T),
    TB_speedMax = base::max(data$TB_speed, na.rm = T),
    TB_distance = base::sum(data$TB_dist, na.rm = T),
    TB_displacement = pull(euclideanDistance(x1 = onsetData$tb_x,
                                        y1 = onsetData$tb_y,
                                        x2 = offsetData$tb_x,
                                        y2 = offsetData$tb_y)),
    # dTB measures
    dTB_speedAvg = base::mean(data$dTB_speed, na.rm = T),
    dTB_speedMax = base::max(data$dTB_speed, na.rm = T),
    dTB_distance = base::sum(data$dTB_dist, na.rm = T),
    dTB_displacement = pull(euclideanDistance(x1 = onsetData$decoupled_tb_x,
                                        y1 = onsetData$decoupled_tb_y,
                                        x2 = offsetData$decoupled_tb_x,
                                        y2 = offsetData$decoupled_tb_y)),
    # Jaw measures
    Jaw_speedAvg = base::mean(data$Jaw_speed, na.rm = T),
    Jaw_speedMax = base::max(data$Jaw_speed, na.rm = T),
    Jaw_distance = base::sum(data$Jaw_dist, na.rm = T),
    Jaw_displacement = pull(euclideanDistance(x1 = onsetData$jaw_x,
                                        y1 = onsetData$jaw_y,
                                        x2 = offsetData$jaw_x,
                                        y2 = offsetData$jaw_y)),
    )
    

    aiMeasures <- aiMeasures %>%
    pull({{measure}})
    
   return(aiMeasures)

}

# /ai/ Acoustic Analysis

# apply the function to each group defined by DatabaseID, condition, and token
aiData_Measures_nested <- aiData_nested %>%
  dplyr::mutate(
    # Acoustic Temporal Info
    onset = map(acoData, ai_aco, measure = onset),
    offset = map(acoData, ai_aco, measure = offset),
    duration = map(acoData, ai_aco, measure = duration),
    # F1 and F2 used to measure acoDistance
    highF2_F1 = map(acoData, ai_aco, measure = highF2_F1),
    highF2_F2 = map(acoData, ai_aco, measure = highF2_F2),
    lowF2_F1 = map(acoData, ai_aco, measure = lowF2_F1),
    lowF2_F2 = map(acoData, ai_aco, measure = lowF2_F2),
    # F2 Slope
    extent = map(acoData, ai_aco, measure = extent),
    F2_Slope = map(acoData, ai_aco, measure = F2_Slope),
    bestFit = map(acoData, ai_aco, measure = bestFit)) %>%
  
  # Now filtering the kinData to only include the transition phase
  unnest(kinData) %>%
  group_by(DatabaseID,Group,condition,phrase,label,token, onset, offset, duration, highF2_F1, highF2_F2, lowF2_F1, lowF2_F2, extent, F2_Slope, bestFit, acoData) %>%
  dplyr::filter(time >= onset & time <= offset) %>%
  nest() %>%
  dplyr::rename(kinData = data) %>%

  # Now calculate the kinematic measures
  dplyr:: mutate(
    # X and Y used to measure kinDistance
    onset_TB_x = map(
      kinData,
      ai_kin,
      measure = onset_TB_x
    ),
    onset_TB_y = map(
      kinData,
      ai_kin,
      measure = onset_TB_y
    ),
    offset_TB_x = map(
      kinData,
      ai_kin,
      measure = offset_TB_x
    ),
    offset_TB_y = map(
      kinData,
      ai_kin,
      measure = offset_TB_y
    ),
    # TB Measures
    TB_speedAvg = map(
      kinData,
      ai_kin,
      measure = TB_speedAvg
    ),
    TB_speedMax = map(
      kinData,
      ai_kin,
      measure = TB_speedMax
    ),
    TB_distance = map(
      kinData,
      ai_kin,
      measure = TB_distance
    ),
    TB_displacement = map(
      kinData,
      ai_kin,
      measure = TB_displacement
    ),
    # dTB Measures
    dTB_speedAvg = map(
      kinData,
      ai_kin,
      measure = dTB_speedAvg
    ),
    dTB_speedMax = map(
      kinData,
      ai_kin,
      measure = dTB_speedMax
    ),
    dTB_distance = map(
      kinData,
      ai_kin,
      measure = dTB_distance
    ),
    dTB_displacement = map(
      kinData,
      ai_kin,
      measure = dTB_displacement
    ),
    # Jaw Measures
    Jaw_speedAvg = map(
      kinData,
      ai_kin,
      measure = Jaw_speedAvg
    ),
    Jaw_speedMax = map(
      kinData,
      ai_kin,
      measure = Jaw_speedMax
    ),
    Jaw_distance = map(
      kinData,
      ai_kin,
      measure = Jaw_distance
    ),
    Jaw_displacement = map(
      kinData,
      ai_kin,
      measure = Jaw_displacement
    ),
  )

aiData_Measures <- aiData_Measures_nested %>%
  dplyr::ungroup() %>%
  dplyr::select(!c(acoData, kinData)) %>%
  unnest() %>%
  group_by(DatabaseID,Group,condition,phrase,label,token) %>%
  dplyr::mutate(acoDistance = pull(euclideanDistance(x1 = highF2_F2,
                                                y1 = highF2_F1,
                                                x2 = lowF2_F2,
                                                y2 = lowF2_F1)),
                kinDistance = pull(euclideanDistance(x1 = onset_TB_x,
                                                y1 = onset_TB_y,
                                                x2 = offset_TB_x,
                                                y2 = offset_TB_y)),
                kinSpeed = kinDistance / duration)


rio::export(x = aiData_Measures,
            file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_aiMeasures.csv")

# Alert that the code is finished running
beepr::beep(sound = 3)
```

## Final Measures
This block cleans up the final Target Measures for analysis
```{r}
speakers <- rio::import(file = "../Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(DatabaseID:Age)

listenerRatings <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings.csv") %>%
  dplyr::select(!1) %>%
  tidyr::pivot_wider(id_cols = c(DatabaseID, condition,Sent, rep),
                     names_from = ratingType,
                     values_from = c(M,SD,Count)) %>%
  dplyr::rename(AP_M = M_AP,
                AP_SD = SD_AP,
                AP_N = Count_AP,
                Int_M = M_Int,
                Int_SD = SD_Int,
                Int_N = Count_Int,
                ) %>%
  dplyr::group_by(DatabaseID, condition, rep) %>%
  dplyr::summarise(Int_M = mean(Int_M, na.rm = T),
                   Int_N = sum(Int_N),
                   AP_M = mean(AP_M, na.rm = T),
                   AP_N = sum(AP_N),
                   )
  
# /ai/ measures
aiMeasures <- rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_aiMeasures.csv") %>%
  dplyr::mutate(kinSpeed = TB_displacement / duration) %>%
  dplyr::select(DatabaseID:duration,
                acoDistance,
                kinDistance,
                F2_Slope,
                TB_speedAvg,
                TB_speedMax,
                TB_distance,
                TB_displacement,
                #dTB_speedAvg,
                #dTB_speedMax,
                #dTB_distance,
                #Jaw_speedAvg,
                #Jaw_speedMax,
                ) %>%
  base::merge(., speakers) %>%
  dplyr::mutate(rep = base::sub(pattern = ".*[.]",
                                     replacement = "",
                                     x = phrase),
                  rep = as.numeric(rep) + 1,
                  rep = case_when(
                    is.na(rep) ~ 1,
                    TRUE ~ rep,
                  )) %>%
  dplyr::relocate(StudyID:Age, .after = DatabaseID) %>%
  base::merge(., listenerRatings, all = T) %>%
  dplyr::relocate(rep, .after = phrase) %>%
  dplyr::relocate(condition, .after = Group) %>%
  
  # Removing instances of "-Inf" and replacing it with NA
  dplyr::mutate(
    TB_speedMax = ifelse(TB_speedMax == "-Inf",NA,TB_speedMax),
    #dTB_speedMax = ifelse(dTB_speedMax == "-Inf",NA,dTB_speedMax),
    TB_distance = ifelse(TB_distance == 0,NA,TB_distance),
    #dTB_distance = ifelse(dTB_distance == 0,NA,dTB_distance),
    ) %>%
  
  # Removing an outlier for TB_speedMax
  dplyr::mutate(TB_speedMax = ifelse(TB_speedMax > 600,NA,TB_speedMax)) %>%
  
  # Removing instances of empty rows
  dplyr::filter(!is.na(onset))

  rio::export(x = aiMeasures, file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv")
  
# VSA Measures ----
  vsaMeasures <- rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/allSpeakers_VSA.csv") %>%
    base::merge(., speakers) %>%
    base::merge(., listenerRatings %>%
                  dplyr::group_by(DatabaseID,condition) %>%
                  dplyr::summarise(
                    Int_M = base::mean(Int_M, na.rm = T),
                    Int_N = base::sum(Int_N, na.rm = T),
                    AP_M = base::mean(AP_M, na.rm = T),
                    AP_N = base::sum(AP_N, na.rm = T),
                    )) %>%
    dplyr::select(DatabaseID, StudyID, Group, Sex, Age, condition, aVSA:kVSA,Int_M:AP_N)
  
  rio::export(x = vsaMeasures, file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv")
```

## Calculating Inter-Reliability
```{r}
# Loading the full data to obtain ranges for each measure.
fullData_VSA <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA, kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData_ai <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(kinSpeed = kinDistance / (duration * 1000)) %>%
  dplyr::select(DatabaseID:token,
                acoDistance,
                kinDistance,
                F2_Slope,
                kinSpeed) %>%
  tidyr::pivot_longer(
    cols = acoDistance:kinSpeed,
    names_to = "Measure",
    values_to = "Value"
  )  %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(range = abs(min(Value, na.rm = T) - max(Value, na.rm = T)))

fullData <- rbind(fullData_ai, fullData_VSA)
rm(fullData_ai, fullData_VSA)

# Diphthong
reliability_ai <- base::merge(
rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(kinSpeed = kinDistance / (duration* 1000)) %>%
  dplyr::select(DatabaseID:token,
                onset, offset,
                acoDistance,
                kinDistance,
                F2_Slope,
                kinSpeed) %>%
    tidyr::pivot_longer(cols = acoDistance:kinSpeed,
                      names_to = "Measure",
                      values_to = "InterRel"),
  
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
      dplyr::mutate(kinSpeed = kinDistance / (duration * 1000)) %>%
      dplyr::select(
        DatabaseID:token,
        onset1 = onset, 
        offset1 = offset,
        acoDistance,
        kinDistance,
        F2_Slope,
        kinSpeed) %>%
    tidyr::pivot_longer(cols = acoDistance:kinSpeed,
                      names_to = "Measure",
                      values_to = "Value"),
#all = T
) %>%
  dplyr::mutate(diff_onset = onset - onset1)


# Calculating ICC
my_icc <- function(data) {
  data %>%
    select(Value, InterRel) %>% # select just the rating columns
    irr::icc(model = "twoway",
             type = "agreement",
             unit = "single") %>%        # calculate the ICC
    unlist() %>%          # turn the output list into a vector
    t() %>%               # transpose this vector
    as_tibble() %>%       # turn the vector into a table 
    select(               # select just the columns you want
      stimuli = subjects, # rename subjects to stimuli     
      raters, 
      icc = value,        # rename value to icc
      lbound, 
      ubound
    ) %>%
    # fix column modes (unlisting turned them all into characters)
    mutate_at(vars(stimuli, raters), as.integer) %>% 
    mutate_at(vars(icc:ubound), as.numeric)
}

# VSA

reliability_vsa <-
  rio::import(file = "../Data/PreppedData/Reliability/Intermeasurer Reliability/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  dplyr::select(DatabaseID:condition, aVSA, kVSA) %>%
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "InterRel") %>%
  base::merge(
    .,
    rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
      dplyr::mutate(aVSA = aVSA / 1000) %>%
      dplyr::select(DatabaseID:condition, aVSA, kVSA) %>%
      tidyr::pivot_longer(
        cols = aVSA:kVSA,
        names_to = "Measure",
        values_to = "Value"
      )
  )

reliability <- rbind(
  reliability_ai %>%
    dplyr::select(
      DatabaseID,
      StudyID,
      Group,
      Age,
      condition,
      Measure,
      Value,
      InterRel
    ),
  reliability_vsa %>%
    dplyr::select(
      DatabaseID,
      StudyID,
      Group,
      Age,
      condition,
      Measure,
      Value,
      InterRel
    )
) %>%
  dplyr::filter(!is.na(Value))

ICC_inter <- reliability %>%
  #dplyr::filter(condition == "conv") %>%
  dplyr::select(Measure, Value, InterRel) %>%
  dplyr::group_by(Measure) %>%
  nest() %>%                                       # nest the rest of the columns
  mutate(icc = map(data, my_icc)) %>%              # calculate ICC for each group
  unnest(icc) %>%                                  # expand the tables returned to icc
  select(-data) %>%
  dplyr::mutate(
    inter_ICC = round(icc, digits = 2),
    inter_lbound = round(lbound, digits = 2),
    inter_ubound = round(ubound, digits = 2),
    APA = paste0(
    Measure, ", ICC(2,A) = ",
    inter_ICC, ", 95% CI [",
    inter_lbound, " - ",
    inter_ubound, "]"
  ))


# Absolute error
absError_ai <- reliability_ai %>%
  dplyr::mutate(absError = abs(Value - InterRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

absError_vsa <- reliability_vsa %>%
  dplyr::mutate(absError = abs(Value - InterRel)) %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(M = mean(absError, na.rm = T),
                   sd = sd(absError, na.rm = T))

inter_absError <- rbind(absError_ai, absError_vsa) %>%
  base::merge(fullData) %>%
  dplyr::mutate(std_absError = M / range)

stats::cor.test(x = reliability$Value,
                y = reliability$InterRel,
                method = "pearson")
```
# Table
```{r}
iccTable <- base::merge(
  
  ICC_intra %>%
    dplyr::select(
      Measure,
      intra_ICC:intra_ubound
    ),
  
  ICC_inter %>%
    dplyr::select(
      Measure,
      inter_ICC:inter_ubound
    ),
)
rio::export(iccTable,
            file = "../Data/PreppedData/Reliability/ICC data.csv")

```

