---
title: "A multidimensional study of articulation deficits in Parkinson’s disease - Data Analysis: Study 2"
---

```{r}
rm(list = ls())
```

# Packages
```{r}
library(tidyverse) # install.packages('tidyverse')
library(emmeans)
library(robustlmm) # install.packages("robustlmm")
library(ggpubr) # install.packages('ggpubr')
library(plyr) # install.packages('plyr')
library(beepr) # install.packages('beepr')
library(plotrix) # install.packages('plotrix')
source('../Functions/MSL Tools.R')
```

# Load Data
```{r}
fileInventories <- rio::import(file = "../Data/RawData/File Inventories.xlsx") %>%
  dplyr::rename(DatabaseID = `Sub #`,
                dxTime = `Time Since Diagnosis`) %>%
  dplyr::select(DatabaseID, dxTime, MoCA)

listenerRatings <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings_allRatings.csv") %>%
  dplyr::filter(ratingType == "Int") %>%
  dplyr::filter(condition == "conv") %>%
  dplyr::group_by(DatabaseID, StudyID) %>%
  dplyr::summarise(Rating_M = mean(Rating, na.rm = T))

speakerList <- rio::import(file = "../Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(!`Folder 2`:`Sentence Repetition`) %>%
  base::merge(., fileInventories) %>%
  base::merge(., listenerRatings) %>%
  
  # Making sure dxTime is numeric
  dplyr::mutate(dxTime = as.numeric(dxTime)) %>%
  
  # Refactoring Sex
  dplyr::mutate(Sex = factor(Sex, 
                             levels = c(
                               "M",
                               "F"
                               ),
                             labels = c(
                               "Male Speakers",
                               "Female Speakers"
                             ))) %>%
  
  # Severity-surrogate ratings
  dplyr::mutate(Severity = case_when(
    Group == "HC" ~ "",
    Rating_M > 94 ~ "Normal",
    between(Rating_M, 85, 94.99) ~ "Mild",
    between(Rating_M, 70, 84.99) ~ "Moderate",
    between(Rating_M, 45, 69.99) ~ "Severe",
    Rating_M < 45 ~ "Profound"
  )) %>%
  
  # Removing the MoCA Scores - Not all speakers had them
  dplyr::select(!MoCA)
```


## Listener Descriptions
```{r}
listenerRatings <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings_allRatings.csv")

ratingCount <- listenerRatings %>%
  dplyr::group_by(StudyID, ratingType) %>%
  dplyr::summarise(n = NROW(Rating)) %>%
  dplyr::ungroup()

ratingCount %>%
  dplyr::summarise(mean = mean(n),
                   sd = sd(n),
                   min = min(n),
                   max = max(n))

NROW(unique(listenerRatings$ListenerID))

listenerDemo <- rio::import(file = "../Data/PreppedData/ListenerData/ListenerDemographics.csv")
NROW(unique(listenerDemo$ListenerID))

# Age and N
listenerDemo %>%
  dplyr::mutate(duration = `Duration (in seconds)`/60) %>%
  #dplyr::group_by(gender) %>%
  dplyr::summarise(age_m = mean(age, na.rm = T),
                   age_sd = sd(age, na.rm = T),
                   min = base::min(age, na.rm = T),
                   max = base::max(age, na.rm = T),
                   N = NROW(age),
                   duration_M = base::mean(duration, na.rm = T),
                   duration_sd = sd(duration, na.rm = T))

listenerDemo %>%
  dplyr::mutate(duration = `Duration (in seconds)`/60) %>%
  dplyr::group_by(gender) %>%
  dplyr::summarise(N = NROW(age))

listenerDemo %>%
  dplyr::mutate(duration = `Duration (in seconds)`/60) %>%
  dplyr::group_by(race) %>%
  dplyr::summarise(N = NROW(race))

listenerDemo %>%
  dplyr::mutate(duration = `Duration (in seconds)`/60) %>%
  dplyr::group_by(ethnicity) %>%
  dplyr::summarise(N = NROW(ethnicity))
```

# APA reporting function
```{r}

apa_lmResults <- function(model, fixedEffect) {
  
coefficients <- summary(model)[["coefficients"]] %>%
  as.data.frame() %>%
  dplyr::rename(
    stdError = `Std. Error`,
    t = `t value`,
    p = `Pr(>|t|)`) %>%
  dplyr::mutate(
    Estimate = round(Estimate, digits = 2),
    #df = round(df, digits = 2),
    t = round(t, digits = 2),
    p = round(p, digits = 3),
  ) %>%
  dplyr::filter(rownames(.) == fixedEffect)

if(coefficients$p < .001) {
  p <- "p<.001"
} else {
  p <- paste0("p=",as.numeric(coefficients$p))
}

df <- as.numeric(model$df.residual)
t <- paste0("t(",df,")=", as.numeric(coefficients$t))

CI_intervals <- stats::confint(model) %>%
  as.data.frame() %>%
  dplyr::mutate(
    ll = round(`2.5 %`, digits = 2),
    ul = round(`97.5 %`, digits = 2),
                ) %>%
  dplyr::select(ll, ul) %>%
  dplyr::filter(rownames(.) == fixedEffect)

CI <- base::paste0("95% CI [",
                  as.numeric(CI_intervals$ll),
                  ", ",
                  as.numeric(CI_intervals$ul),
                  "]")

formula <- paste(t, p, CI, sep = ", ")

return(formula)

rm(coefficients, t, p, CI_intervals, CI)
}

apa_lmeResults <- function(model, fixedEffect) {
  
coefficients <- summary(model)[["coefficients"]] %>%
  as.data.frame() %>%
  dplyr::rename(
    stdError = `Std. Error`,
    t = `t value`,
    p = `Pr(>|t|)`) %>%
  dplyr::mutate(
    Estimate = round(Estimate, digits = 2),
    df = round(df, digits = 2),
    t = round(t, digits = 2),
    p = round(p, digits = 3),
  ) %>%
  dplyr::filter(rownames(.) == fixedEffect)

if(coefficients$p < .001) {
  p <- "p<.001"
} else {
  p <- paste0("p=",as.numeric(coefficients$p))
}

t <- paste0("t(",as.numeric(coefficients$df),")=", as.numeric(coefficients$t))

CI_intervals <- stats::confint(model) %>%
  as.data.frame() %>%
  dplyr::mutate(
    ll = round(`2.5 %`, digits = 2),
    ul = round(`97.5 %`, digits = 2),
                ) %>%
  dplyr::select(ll, ul) %>%
  dplyr::filter(rownames(.) == fixedEffect)

CI <- base::paste0("95% CI [",
                  as.numeric(CI_intervals$ll),
                  ", ",
                  as.numeric(CI_intervals$ul),
                  "]")

formula <- paste(t, p, CI, sep = ", ")

return(formula)

rm(coefficients, t, p, CI_intervals, CI)
}

apa_levelDescriptives <- function(data,level, outcome) {

  
descriptiveData <- modelData %>%
  dplyr::select(Group, Sex, sym(outcome)) %>%
  dplyr::rename(outcome = 3)

group <- descriptiveData %>%
  dplyr::group_by(Group) %>%
  dplyr::summarize(M = mean(outcome, na.rm = T),
                SD = sd(outcome, na.rm = T),
                .groups = 'drop') %>%
  dplyr::mutate(M = round(M, digits = 2),
                SD = round(SD, digits = 2)) %>%
  dplyr::rename(Grouping = 1) %>%
  as.data.frame()

sex <- descriptiveData %>%
  dplyr::group_by(Sex) %>%
  dplyr::summarize(M = mean(outcome, na.rm = T),
                SD = sd(outcome, na.rm = T),
                .groups = 'drop') %>%
  dplyr::mutate(M = round(M, digits = 2),
                SD = round(SD, digits = 2)) %>%
  dplyr::rename(Grouping = 1) %>%
  as.data.frame()

groupSex <- descriptiveData %>%
  dplyr::group_by(Group, Sex) %>%
  dplyr::summarize(M = mean(outcome, na.rm = T),
                SD = sd(outcome, na.rm = T),
                .groups = 'drop') %>%
  dplyr::ungroup() %>%
  dplyr::mutate(M = round(M, digits = 2),
                SD = round(SD, digits = 2),
                Grouping = paste(Group, Sex, sep = "_")) %>%
  dplyr::select(Grouping, M, SD) %>%
  as.data.frame()

descriptives <- rbind(group,
                      sex,
                      groupSex) %>%
  dplyr::filter(Grouping == level)
  
  output <- paste0(level,": (M=",descriptives$M,", SD=",descriptives$SD,")")
  
  return(output)
  
  rm(descriptives, group, sex, groupSex)
  
}


apa_emmsPairs <- function(emmsPair, sex, Condition) {
  summary_table <- summary(emmsPair, infer = TRUE) %>%
    dplyr::filter(Sex == sex) %>%
    dplyr::filter(condition == condition)
  
if(summary_table$p.value < .001) {
  p <- "p < .001"
} else {
    p <- paste0("p=",
                round(summary_table$p.value, digits = 3))
  }
  
  if("t.ratio" %in% colnames(summary_table)) {
  output <- paste(
    sex,
    ", HC - PD: (",
    "t(",
    round(summary_table$df, digits = 2),
    ")=",
    as.numeric(round(summary_table$t.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  
  if("z.ratio" %in% colnames(summary_table)) {
  output <- paste(
    sex,
    ", HC - PD: (",
    "z = (",
    as.numeric(round(summary_table$z.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  return(output)
}

apa_s1_emmPairs <- function(emmsPair, sex, Condition) {
  summary_table <- summary(emmsPair, infer = TRUE) %>%
    dplyr::filter(Sex == sex) %>%
    dplyr::filter(condition == Condition)
  
  if(summary_table$p.value < .001) {
  p <- "p<.001"
} else {
    p <- paste0("p=",
                round(summary_table$p.value, digits = 3))
  }
  
  if("t.ratio" %in% colnames(summary_table)) {
  output <- paste(
    sex,
    ", HC - PD: (",
    "t(",
    round(summary_table$df, digits = 2),
    ")=",
    as.numeric(round(summary_table$t.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  
  if("z.ratio" %in% colnames(summary_table)) {
  output <- paste(
    sex,
    ", HC - PD: (",
    "z=",
    as.numeric(round(summary_table$z.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  return(output)
}

apa_s2_emmPairs <- function(emmsPair, Sex_Input, Group_Input, Contrast_Input) {
  summary_table <- summary(emmsPair, infer = TRUE) %>%
    dplyr::filter(Sex == Sex_Input) %>%
    dplyr::filter(Group == Group_Input) %>%
    dplyr::filter(contrast == Contrast_Input)
  
  if(summary_table$p.value < .001) {
  p <- "p<.001"
} else {
    p <- paste0("p=",
                round(summary_table$p.value, digits = 3))
  }
  
  if("t.ratio" %in% colnames(summary_table)) {
  output <- paste(
    Sex_Input,
    ", ",
    Group_Input,
    ", ",
    Contrast_Input,
    ": (",
    "t(",
    round(summary_table$df, digits = 2),
    ")=",
    as.numeric(round(summary_table$t.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  
  if("z.ratio" %in% colnames(summary_table)) {
  output <- paste(
    Sex_Input,
    ", ",
    Group_Input,
    ", ",
    Contrast_Input,
    ": (",
    "z=",
    as.numeric(round(summary_table$z.ratio, 2)),
    ", ",
    p,
    ")",
    sep = "")
  }
  
  return(output)
}



```


# RQ1 - Correlations
1.	What is the nature and extent of the relationships between perceptual, acoustic, and kinematic measures across conversational, less clear, and more clear speaking conditions?
    a.	What is the relationship between intelligibility and articulatory precision ratings?
    b.	What is the relationship between acoustic measures and their underlying theoretical kinematic measures (i.e., acoustic VSA vs. kinematic VSA, acoustic distance vs. kinematic distance, F2 slope vs. kinematic speed)?
```{r}
vsaMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F")),
                aVSA = aVSA/1000)

aiMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F")))
```


### 1A - Int & AP
What is the relationship between intelligibility and articulatory precision ratings?
```{r}

# VSA Data
stats::cor.test(x = vsaMeasures$Int_M,
                y = vsaMeasures$AP_M,
                method = "pearson")

# Diphthong Data
stats::cor.test(x = aiMeasures$Int_M,
                y = aiMeasures$AP_M,
                method = "pearson")

```

## Correlations
```{r}

# VSA Data
corrr::correlate(vsaMeasures %>% dplyr::select(Int_M, AP_M, aVSA, kVSA))

# Diphthong Data
corrr::correlate(aiMeasures %>% 
                               dplyr::select(Int_M,
                                             AP_M,
                                             acoDistance,
                                             F2_Slope,
                                             kinDistance,
                                             kinSpeed),
                             method = "pearson")


stats::cor.test(x = vsaMeasures$aVSA,
                y = vsaMeasures$kVSA,
                method = "pearson")
```
# RQ2 - Models
2.	What is the relationship between the selected acoustic/kinematic measures and perceptual ratings of speech intelligibility and articulatory precision across the three speaking conditions?
## 1. Point-Based Measures
```{r}
vsaMeasures <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M", "F")),
                aVSA = aVSA / 1000)

modelData <- vsaMeasures %>%
  dplyr::rename(SpeakerID = StudyID)

# Taking out the trash
rm(vsaMeasures)
```

### Intelligibility
M1 - Comprehensive Model
```{r}
Int_PBS_m1 <- robustlmm::rlmer(Int_M ~
                                 aVSA * Sex +
                                 #kVSA * Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(Int_PBS_m1)
```
We can see that only the aVSA, Sex, and aVSA x Sex predictors were significant. So we will only retain those in the most parsimonious model.

M2
```{r}
Int_PBS_m2 <- robustlmm::rlmer(Int_M ~
                                 aVSA * Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(Int_PBS_m2)
```

Final Model
```{r}
Int_PBS <- Int_PBS_m2

summary(Int_PBS)
sjPlot::tab_model(Int_PBS)

# Saving the model
base::saveRDS(object = Int_PBS,
              file = "Models/Int_PBS.rds")

# Taking out the trash
rm(list = ls(pattern = "^Int_m"))
rm(list = ls(pattern = "^emms_"))
```

### Articulatory Precision
M1 - Comprehensive Model
```{r}
AP_PBS_m1 <- robustlmm::rlmer(AP_M ~
                                aVSA * Sex +
                                kVSA * Sex +
                                (1 | SpeakerID),
                              data = modelData)

sjPlot::tab_model(AP_PBS_m1)
```
We can see that only the aVSA, Sex, and aVSA x Sex predictors were significant. So we will only retain those in the most parsimonious model.

M2
```{r}
AP_PBS_m2 <- robustlmm::rlmer(AP_M ~
                                 aVSA * Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(AP_PBS_m2)
```

Final Model
```{r}
AP_PBS <- AP_PBS_m2

summary(AP_PBS)
sjPlot::tab_model(AP_PBS)

# Saving the model
base::saveRDS(object = AP_PBS,
              file = "Models/AP_PBS.rds")

# Taking out the trash
rm(list = ls(pattern = "^AP_m"))
rm(list = ls(pattern = "^emms_"))
```

### Saving Models
Saving the models for the table
```{r}
base::saveRDS(Int_PBS_m1, file = "Models/Int_PBS_m1.rds")
base::saveRDS(AP_PBS_m1, file = "Models/AP_PBS_m1.rds")
```

## 2. Transition-Based Measures
```{r}
aiMeasures <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M", "F")))

modelData <- aiMeasures %>%
  dplyr::rename(SpeakerID = StudyID)

# Taking out the trash
rm(aiMeasures)
```

### Intelligibility
M1 - Comprehensive Model
```{r}
Int_TBS_m1 <- robustlmm::rlmer(Int_M ~
                                 acoDistance * Sex +
                                 kinDistance * Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(Int_TBS_m1)
```
We can see that only the kinDistance, and Sex were significant. So we will only retain those in the most parsimonious model.

M2
```{r}
Int_TBS_m2 <- robustlmm::rlmer(Int_M ~
                                 kinDistance +
                                 Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(Int_TBS_m2)
```

Final Model
```{r}
Int_TBS <- Int_TBS_m2

summary(Int_TBS)
sjPlot::tab_model(Int_TBS)

# Saving the model
base::saveRDS(object = Int_TBS,
              file = "Models/Int_TBS.rds")

# Taking out the trash
rm(list = ls(pattern = "^Int_m"))
rm(list = ls(pattern = "^emms_"))
```
### Articulatory Precision
M1 - Comprehensive Model
```{r}
AP_TBS_m1 <- robustlmm::rlmer(AP_M ~
                                 acoDistance * Sex +
                                 kinDistance * Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(AP_TBS_m1)
```
We can see that only the kinDistance, and Sex were significant. So we will only retain those in the most parsimonious model.

M2 - Comprehensive Model
```{r}
AP_TBS_m2 <- robustlmm::rlmer(AP_M ~
                                 kinDistance +
                                 Sex +
                                 (1 | SpeakerID),
                               data = modelData)

sjPlot::tab_model(AP_TBS_m2)
```

Final Model
```{r}
AP_TBS <- AP_TBS_m2

summary(AP_TBS)
sjPlot::tab_model(AP_TBS)

# Saving the model
base::saveRDS(object = AP_TBS,
              file = "Models/AP_TBS.rds")

# Taking out the trash
rm(list = ls(pattern = "^AP_m"))
rm(list = ls(pattern = "^emms_"))
```
### Saving Models
Saving the models for the table
```{r}
base::saveRDS(Int_TBS_m1, file = "Models/Int_TBS_m1.rds")
base::saveRDS(AP_TBS_m1, file = "Models/AP_TBS_m1.rds")
```

## 3. Spatiotemporal Measures
```{r}
aiMeasures <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M", "F")))

modelData <- aiMeasures %>%
  dplyr::rename(SpeakerID = StudyID)

# Taking out the trash
rm(aiMeasures)
```

### Intelligibility
M1
```{r}
# Building the model
Int_SpaTemp_m1 <- robustlmm::rlmer(Int_M ~
                                     F2_Slope * Sex +
                                     kinSpeed * Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(Int_SpaTemp_m1)
```
Only sex was a significant predictor of intelligibility.

M2
```{r}
# Building the model
Int_SpaTemp_m2 <- robustlmm::rlmer(Int_M ~
                                     F2_Slope +
                                     kinSpeed +
                                     Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(Int_SpaTemp_m2)
```

M3
```{r}
# Building the model
Int_SpaTemp_m3 <- robustlmm::rlmer(Int_M ~
                                     Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(Int_SpaTemp_m3)
```

Final Model
```{r}
Int_SpaTemp <- Int_SpaTemp_m3

summary(Int_SpaTemp)
sjPlot::tab_model(Int_SpaTemp)

# Saving the model
base::saveRDS(object = Int_SpaTemp,
              file = "Models/Int_SpaTemp.rds")

# Taking out the trash
rm(list = ls(pattern = "^Int_m"))
rm(list = ls(pattern = "^emms_"))
```

### Articulatory Precision
M1
```{r}
# Building the model
AP_SpaTemp_m1 <- robustlmm::rlmer(AP_M ~
                                     F2_Slope * Sex +
                                     kinSpeed * Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(AP_SpaTemp_m1)
```
Only sex was a significant predictor of articulatory precision

M2
```{r}
# Building the model
AP_SpaTemp_m2 <- robustlmm::rlmer(AP_M ~
                                     F2_Slope +
                                     kinSpeed +
                                     Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(AP_SpaTemp_m2)
```
Removing the sex interactions revealed that F2 slope appears to be a meaningful predictor of articulatory precision. Let's continue to remove non significant variables to obtain the most parsimonious model.

M3
```{r}
# Building the model
AP_SpaTemp_m3 <- robustlmm::rlmer(AP_M ~
                                     F2_Slope +
                                     Sex +
                                     (1 | SpeakerID),
                                   data = modelData)
# Model summary
sjPlot::tab_model(AP_SpaTemp_m3)
```

Final Model
```{r}
AP_SpaTemp <- AP_SpaTemp_m3

summary(AP_SpaTemp)
sjPlot::tab_model(AP_SpaTemp)

# Saving the model
base::saveRDS(object = AP_SpaTemp,
              file = "Models/AP_SpaTemp.rds")

# Taking out the trash
rm(list = ls(pattern = "^AP_m"))
rm(list = ls(pattern = "^emms_"))
```

### Saving Models
Saving the models for the table
```{r}
base::saveRDS(Int_SpaTemp_m1, file = "Models/Int_SpaTemp_m1.rds")
base::saveRDS(Int_SpaTemp_m2, file = "Models/Int_SpaTemp_m2.rds")
base::saveRDS(AP_SpaTemp_m1, file = "Models/AP_SpaTemp_m1.rds")
base::saveRDS(AP_SpaTemp_m2, file = "Models/AP_SpaTemp_m2.rds")
```

## Comparing Models
```{r}
# VSA ----
## Fit model 1
model1 <- Int_VSA_finalModel
## Fit model 2
model2 <- AP_VSA_finalModel

## Compare R-squared values
r_squared1 <- summary(model1)$r.squared
r_squared2 <- summary(model2)$r.squared

## Compare the R-squared values
cat("R-squared for model 1:", r_squared1, "\n")
cat("R-squared for model 2:", r_squared2, "\n")

# kinDistance ----
library(MuMIn) # install.packages('MuMIn')

## Fit model 1
model1 <- Int_ai_finalModel
## Fit model 2
model2 <- AP_ai_finalModel

## Compare R-squared values
r_squared1 <- MuMIn::r.squaredGLMM(model1)[2]
r_squared2 <- MuMIn::r.squaredGLMM(model2)[2]

## Compare the R-squared values
cat("R-squared for model 1 (Int):", r_squared1, "\n")
cat("R-squared for model 2 (AP):", r_squared2, "\n")
```

# Plots
```{r}
myPal <- rcartocolor::carto_pal(n = 7, name = "Geyser")[c(1, 2, 3, 4, 5, 6, 7)]
color_HC <- myPal[2] 
color_PD <- myPal[6]
```

## 1. Int & AP ~ VSA
```{r}
# Just scatter plot ----
plot_VSA_data <- rio::import(file = "Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
dplyr::mutate(Sex = factor(Sex,
                             levels = c("M",
                                        "F"),
                             labels = c("Male Speakers",
                                        "Female Speakers")
                             ),
                Condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less\nClear",
                                     "Conversational",
                                     "More\nClear"
                                   ))) %>%
  tidyr::pivot_longer(cols = c(Int_M,AP_M),
                      names_to = "ratingType",
                      values_to = "Rating") %>%
  dplyr::mutate(ratingType = factor(ratingType,
                                    levels = c("Int_M","AP_M"),
                                    labels = c("Intelligibility (VAS)",
                                               "Articulatory Precision (VAS)")),
                aVSA = aVSA/1000)


  
# Making the Plot
plot_VSA <- plot_VSA_data %>%
  ggplot() +
  aes(y = Rating,
      x = aVSA) +
  geom_point(aes(
    shape = Condition,
    color = Group),
    alpha = 1) +
  geom_smooth(method = "lm",
              color = "#2A2A28",
              linetype = 2,
              alpha = .2,
              ) +
  
  # Facet by Sex
  facet_grid(ratingType ~ Sex,
             scales = "free_x") +
  
  # Changing the y axis scale
  #coord_cartesian(ylim = c(0,850)) +
  #scale_y_continuous(breaks=c(0, 25, 50, 75, 100)) +
  
  # Changing the theme, labels, and title
  theme_minimal() +
  labs(x = bquote('Acoustic VSA (kHz'^2*")")) +
  #ggtitle("Acoustic VSA") +
  theme(
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5),
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_blank(),
    ) +

  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD)) +
  scale_shape_manual(values = c(17, 16, 15))

plot_VSA

# Scatter plot + Model Predictions ----
  modelData <- rbind(Int_VSA_finalModel@frame %>%
                      dplyr::mutate(fit = predict(Int_VSA_finalModel),
                                    ratingType = "Int") %>%
                      dplyr::rename(Rating = Int_M),
                    AP_VSA_finalModel@frame %>%
                      dplyr::mutate(fit = predict(AP_VSA_finalModel),
                                    ratingType = "AP") %>%
                      dplyr::rename(Rating = AP_M)) %>%
  dplyr::select(!Sex) %>%
  dplyr::mutate(ratingType = case_when(
    ratingType == "Int" ~ "Intelligibility (VAS)",
    ratingType == "AP" ~ "Articulatory Precision (VAS)"
  )) %>%
  base::merge(., plot_VSA_data) %>%
  dplyr::mutate(Condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less\nClear",
                                     "Conversational",
                                     "More\nClear"
                                   )),
                ratingType = factor(ratingType,
                                    levels = c(
                                      "Intelligibility (VAS)",
                                      "Articulatory Precision (VAS)"
                                    )))
  
plot_VSA_modelData <- modelData %>%
  ggplot() +
  aes(y = Rating,
      x = aVSA) +
  
  # Adding the points
  geom_point(aes(
    shape = Condition,
    color = Group
    ),
    alpha = .3) +

  # Adding the model prediction lines
  geom_line(aes(y = fit,
                x = aVSA,
                group = StudyID,
                color = Group),
            size = .8) +
  
  # Facet by Sex
  facet_grid(ratingType ~ Sex,
             scales = "free_x") +

  
  # Changing the theme, labels, and title
  theme_minimal() +
  labs(x = bquote('Acoustic VSA (kHz'^2*")")) +
  #ggtitle("Acoustic VSA") +
  theme(
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5),
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_blank(),
    ) +

  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD)) +
  scale_shape_manual(values = c(17, 16, 15))

plot_VSA_modelData
```

## 2. Int & AP ~ kinDistance
```{r}
# Just scatter plots ----
plot_ai_data <- rio::import(file = "Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex,
                             levels = c("M",
                                        "F"),
                             labels = c("Male Speakers",
                                        "Female Speakers")
                             ),
                Condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less\nClear",
                                     "Conversational",
                                     "More\nClear"
                                   ))) %>%
  tidyr::pivot_longer(cols = c(Int_M,AP_M),
                      names_to = "ratingType",
                      values_to = "Rating") %>%
  dplyr::mutate(ratingType = factor(ratingType,
                                    levels = c("Int_M","AP_M"),
                                    labels = c("Intelligibility (VAS)",
                                               "Articulatory Precision (VAS)")))


# Making the Plot
plot_ai <- plot_ai_data %>%
  ggplot() +
  aes(y = Rating,
      x = kinDistance) +
  geom_point(aes(
    shape = Condition,
    color = Group),
    alpha = .8) +
  geom_smooth(
    method = "lm",
              color = "#2A2A28",
              linetype = 2,
              alpha = .2,
              ) +
  
  # Facet by Sex
  facet_grid(ratingType~Sex,
             scales = "free_x") +
  
  # Changing the theme, labels, and title
  theme_minimal() +
  labs(x = bquote('Kinematic (TB) Distance (mm'^2*")")) +
  theme(
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5),
    #axis.text.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_blank(),
    ) +

  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD)) +
  scale_shape_manual(values = c(17, 16, 15))

plot_ai

# Scatter plot + Model Predictions  ----
## Get the model data
  modelData <- rbind(Int_ai_finalModel@frame %>%
                      dplyr::mutate(fit = predict(Int_ai_finalModel),
                                    ratingType = "Int") %>%
                      dplyr::rename(Rating = Int_M),
                    AP_ai_finalModel@frame %>%
                      dplyr::mutate(fit = predict(AP_ai_finalModel),
                                    ratingType = "AP") %>%
                      dplyr::rename(Rating = AP_M)) %>%
  dplyr::select(!Sex) %>%
  dplyr::mutate(ratingType = case_when(
    ratingType == "Int" ~ "Intelligibility (VAS)",
    ratingType == "AP" ~ "Articulatory Precision (VAS)"
  )) %>%
  base::merge(., plot_ai_data) %>%
  dplyr::mutate(Condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less\nClear",
                                     "Conversational",
                                     "More\nClear"
                                   )),
                ratingType = factor(ratingType,
                                    levels = c(
                                      "Intelligibility (VAS)",
                                      "Articulatory Precision (VAS)"
                                    )))



## Making the Plot
plot_ai_speakerSlopes <- modelData %>%
  ggplot() +
  aes(y = Rating,
      x = kinDistance) +
  geom_point(aes(
    shape = Condition,
    color = Group
    ),
    alpha = .3) +

  # Adding the model prediction lines
  geom_line(aes(y = fit,
                x = kinDistance,
                group = StudyID,
                color = Group),
            size = .8) +
  
  # Facet by Sex
  facet_grid(ratingType~Sex,
             scales = "free_x") +
  
  
  # Changing the theme, labels, and title
  theme_minimal() +
  labs(x = bquote('Kinematic (TB) Distance (mm'^2*")")) +
  #ggtitle("Acoustic VSA") +
  theme(
    aspect.ratio = 1,
    plot.title = element_text(hjust = 0.5),
    axis.title.y = element_blank(),
    ) +

  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD)) +
  scale_shape_manual(values = c(17, 16, 15))

plot_ai_speakerSlopes

```

## Scatterplots
```{r}
plot_scatterplot_ai <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex,
                             levels = c("M",
                                        "F"),
                             labels = c("Male Speakers",
                                        "Female Speakers")
                             ),
                Condition = factor(condition,
                                   levels = c(
                                     "lessClear",
                                     "conv",
                                     "moreClear"
                                   ),
                                   labels = c(
                                     "Less Clear",
                                     "Conversational",
                                     "More Clear"
                                   ))) %>%
  tidyr::pivot_longer(cols = c(Int_M,AP_M),
                      names_to = "ratingType",
                      values_to = "Rating") %>%
  dplyr::mutate(ratingType = factor(ratingType,
                                    levels = c("Int_M","AP_M"),
                                    labels = c("Intelligibility (VAS)",
                                               "Articulatory Precision (VAS)"))) %>%
  dplyr::select(StudyID, Sex, Group, condition, rep,
                ratingType, Rating,
                acoDistance, kinDistance,
                F2_Slope, kinSpeed) %>%
  tidyr::pivot_longer(cols = c(acoDistance, kinDistance,
                F2_Slope, kinSpeed),
                names_to = "Measure",
                values_to = "Value")

plot_scatterplot_ai %>%
  dplyr::filter(Sex == "Male Speakers") %>%
  
  # Making the plot
  ggplot() +
  aes(x = Value,
      y = Rating) +
  
  # Adding the points
  geom_point(aes(color = Group,
                 shape = condition),
             alpha = .9) +
  
  # Adding the "lm" smoothed regression line
    geom_smooth(method = "lm",
              color = "#2A2A28",
              linetype = 2,
              alpha = .2,
              ) +
  
  # Faceting by Perceptual measure and Target Measures
  facet_grid(ratingType ~ Measure, scales = "free") +
  
  # Making the perceptual measures range from 0-100
  lims(y = c(0,100)) +
  
  # Adding a title
  ggtitle(label = "Male Speakers") +
  
  # Changing the color & point shape
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD)) +
  scale_shape_manual(values = c(17, 16, 15)) +

  # Modifying the theme
  theme_minimal() +
  theme(aspect.ratio = 1)

ggsave(filename = "S3_Scatterplots_male speakers.png",
       plot = last_plot(),
       path = "Data/Plots/Results",
       height = 3.5,
       width = 8,
       units = "in",
       scale = 1.3)
```
## Correlation Table
```{r}
library(ggcorrplot) # install.packages("ggcorrplot")

  # aI Measures ----
aiMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F")))

corTable <- corrr::correlate(aiMeasures %>%
                               dplyr::select(Int_M,
                                             AP_M,
                                             acoDistance,
                                             F2_Slope,
                                             kinDistance,
                                             kinSpeed
                                             ) %>%
                               dplyr::rename(`Intelligibility` = Int_M,
                                             `Articulatory Precision` = AP_M,
                                             `Acoustic Distance` = acoDistance,
                                             `F2 Slope` = F2_Slope,
                                             `Kinematic Distance` = kinDistance,
                                             `Kinematic Speed` = kinSpeed),
                             method = "pearson", diagonal = 1) %>%
  dplyr::mutate_at(.vars = c("Intelligibility",
                             "Articulatory Precision",
                             "Acoustic Distance",
                             "Kinematic Distance",
                             "F2 Slope",
                             "Kinematic Speed"),
                   .funs = round,
                   digits = 2) %>%
  column_to_rownames(var = "term")

corrPlot_ai <- ggcorrplot(
    corTable,
    hc.order = TRUE,
    type = "lower",
    outline.col = "white",
    lab = TRUE,
    ggtheme = ggplot2::theme_classic) +
    scale_fill_gradient2(limit = c(-0.5,1),
                         low = color_PD,
                         high =  color_HC,
                         mid = "white",
                         midpoint = 0,
                         name = "Correlation\nCoefficient\n")
  
  
  # VSA Measures ----
vsaMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  dplyr::mutate(Sex = factor(Sex, levels = c("M","F")))

corTable <- corrr::correlate(vsaMeasures %>%
                               dplyr::select(Int_M,
                                             AP_M,
                                             aVSA,
                                             kVSA,
                                             ) %>%
                               dplyr::rename(`Intelligibility` = Int_M,
                                             `Articulatory Precision` = AP_M,
                                             `Acoustic VSA` = aVSA,
                                             `Kinematic VSA` = kVSA),
                             method = "pearson", diagonal = 1) %>%
  dplyr::mutate_at(.vars = c("Intelligibility",
                             "Articulatory Precision",
                             "Acoustic VSA",
                             "Kinematic VSA"),
                   .funs = round,
                   digits = 2) %>%
  column_to_rownames(var = "term") %>%
  dplyr::mutate(`Acoustic VSA` = `Acoustic VSA`/1000)

corrPlot_vsa <- ggcorrplot(
    corTable,
    hc.order = F,
    type = "lower",
    outline.col = "white",
    lab = TRUE,
    ggtheme = ggplot2::theme_classic) +
    scale_fill_gradient2(limit = c(-0.5,1),
                         low = color_PD,
                         high =  color_HC,
                         mid = "white",
                         midpoint = 0,
                         name = "Correlation\nCoefficient\n")
  

  
  corrPlot <- corrPlot_vsa + corrPlot_ai + patchwork::plot_layout(guides = "collect")
  corrPlot
  
  

```
# Plots
## Motor Equivilance Plot
PDM04 - PDM06
```{r}
aiMeasures <- rio::import(file = "Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv")

speakers <- aiMeasures %>%
  dplyr::select(StudyID, Sex, Group, Age) %>%
  base::unique()

speakerContrast <- aiMeasures %>%
  dplyr::filter(condition == "conv") %>%
  dplyr::filter(StudyID == "HCF03" | StudyID == "HCF05") %>%
  dplyr::mutate(duration = duration*1000)

speakerContrast_pair1 <- rbind(
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "PDM04" & rep == 4),
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "PDM06" & rep == 5)
)

speakerContrast_pair2 <- rbind(
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCF03" & rep == 2),
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCF05" & rep == 1)
)

speakerContrast_pair3 <- rbind(
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM06" & rep == 4), # 4 is good
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM07" & rep == 2) # 2 is good
)

speakerContrast_pair4 <- rbind(
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM07" & rep == 3),
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM08" & rep == 1)
)

speakerContrast_pair5 <- rbind(
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM05" & rep == 1),
  aiMeasures %>%
    dplyr::filter(condition == "conv") %>%
    dplyr::filter(StudyID == "HCM08" & rep == 2)
)


targetContrastPair <- speakerContrast_pair4
speaker1 <- targetContrastPair %>%
  dplyr::filter(row_number() == 1)
speaker2 <- targetContrastPair %>%
  dplyr::filter(row_number() == 2)

# Acoustic Data
acousticSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                            speaker2$offset))


plot_acousticSegment <- acousticSegments %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(time = time - min(time)) %>%
  ggplot() +
  aes(x = F2,
      y = F1,
      alpha = time) +
  geom_path() +
  geom_point() +
  scale_y_reverse() +
  facet_wrap(~DatabaseID) +
  theme_minimal() +
  theme(aspect.ratio = 1)
plot_acousticSegment

# Movement Data
movementSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                            speaker2$offset))

plot_movementSegments <- movementSegments %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(time = time - min(time),
                tb_x = scale(tb_x, center = T, scale = F)) %>%
  ggplot() +
  aes(x = tb_x,
      y = tb_y,
      alpha = time) +
  geom_path() +
  geom_point() +
  facet_wrap(~DatabaseID) +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  labs(x = "Posterior-Anterior (x)",
       y = "Inferior-Superior (y)")
plot_movementSegments

library(patchwork)
plot_speakerContrast <- plot_acousticSegment +
  plot_movementSegments +
  patchwork::plot_layout(ncol = 1)
plot_speakerContrast
```

# Contrast - 1 dimension
```{r}
targetContrastPair <- speakerContrast_pair5
speaker1 <- targetContrastPair %>%
  dplyr::filter(row_number() == 1)
speaker2 <- targetContrastPair %>%
  dplyr::filter(row_number() == 2)


# Acoustic Data
acousticSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                            speaker2$offset))
# Movement Data
movementSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                           speaker2$offset))

# Combining data
plotData <- rbind(acousticSegments %>%
                    dplyr::group_by(DatabaseID) %>%
                    dplyr::mutate(time = time - min(time),
                                  xlab = "Acoustic (F2)") %>%
                    dplyr::select(DatabaseID, time, xlab, F2) %>%
                    dplyr::rename(x = F2),
                  
                  movementSegments %>%
                    dplyr::group_by(DatabaseID) %>%
                    dplyr::mutate(time = time - min(time),
                                  xlab = "Movement (x)") %>%
                  dplyr::select(DatabaseID, time, xlab, tb_x) %>%
                    dplyr::rename(x = tb_x)) %>%
  dplyr::group_by(DatabaseID, xlab) %>%
  dplyr::mutate(x = scale(x, center = T, scale = F))



plot <- plotData %>%
  ggplot() +
  aes(x = time,
      y = x,
      alpha = time) +
  geom_path() +
  geom_point() +
  facet_grid(xlab~DatabaseID,
             scales = "free_y") +
  theme_classic() +
  theme(aspect.ratio = 1) +
  labs(x = "time",
       y = "Inferior-Superior Dimension")
plot

```
# Contrast - all Movement
```{r}
targetContrastPair <- speakerContrast_pair4
speaker1 <- targetContrastPair %>%
  dplyr::filter(row_number() == 1)
speaker2 <- targetContrastPair %>%
  dplyr::filter(row_number() == 2)

# Acoustic Data
acousticSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_AcousticSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                            speaker2$offset))


plot_acousticSegment <- acousticSegments %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(time = time - min(time)) %>%
  ggplot() +
  aes(x = time,
      y = F2,
      alpha = time) +
  geom_path() +
  geom_point() +
  #scale_y_reverse() +
  facet_wrap(~DatabaseID) +
  theme_classic() +
  theme(aspect.ratio = 1)
plot_acousticSegment

# Movement Data
movementSegments <- rio::import(file = "Data/PreppedData/CollatedData/allSpeakers_MovementSegments.csv") %>%
  dplyr::filter(DatabaseID == speaker1$DatabaseID & between(time,
                                                            speaker1$onset,
                                                            speaker1$offset) |
                  DatabaseID == speaker2$DatabaseID & between(time,
                                                            speaker2$onset,
                                                            speaker2$offset)) %>%
  dplyr::select(DatabaseID, time,
                tb_x, tb_y,
                tf_x, tf_y,
                ul_x, ul_y,
                ll_x, ll_y,
                jaw_x, jaw_y)
x <- movementSegments %>%
  dplyr::select(DatabaseID, time, tb_x, tf_x, ul_x,ll_x, jaw_x) %>%
  tidyr::pivot_longer(cols = tb_x:jaw_x,
                      names_to = "Articulator",
                      values_to = "x") %>%
  dplyr::mutate(Articulator = gsub(pattern = "_x",
                                   replacement = "",
                                   x = Articulator))

y <- movementSegments %>%
  dplyr::select(DatabaseID, time, tb_y, tf_y, ul_y,ll_y, jaw_y) %>%
  tidyr::pivot_longer(cols = tb_y:jaw_y,
                      names_to = "Articulator",
                      values_to = "y") %>%
  dplyr::mutate(Articulator = gsub(pattern = "_y",
                                   replacement = "",
                                   x = Articulator))

movementSegments <- base::merge(x, y)

plot_movementSegments <- movementSegments %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(time = time - min(time)) %>%
  ggplot() +
  aes(x = x,
      y = y,
      color = Articulator,
      alpha = time) +
  geom_path() +
  geom_point() +
  facet_wrap(~DatabaseID) +
  theme_classic() +
  theme(aspect.ratio = 1) +
  labs(x = "x",
       y = "Inferior-Superior (y)")
plot_movementSegments


library(patchwork)
plot_speakerContrast <- plot_acousticSegment +
  plot_movementSegments +
  plot_movementSegments_tf +
  patchwork::plot_layout(ncol = 1)
plot_speakerContrast
```

# aVSA vs. kVSA
```{r}
myPal <- rcartocolor::carto_pal(n = 7, name = "Geyser")[c(1, 2, 3, 4, 5, 6, 7)]
color_HC <- myPal[2] 
color_PD <- myPal[6]

speakers <- rio::import(file = "../Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(DatabaseID:Sex)

vsaMeasures <- rio::import(file = "../Data/PreppedData/CollatedData/allSpeakers_tempMid.csv") %>%
  dplyr::select(DatabaseID, Group, condition, label,
                F1_tempMid, F2_tempMid,
                TB_x_tempMid, TB_y_tempMid) %>%
  base::merge(., speakers, no.dups = F) %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(TB_x_tempMid = scale(TB_x_tempMid, center = T, scale = F),
                TB_y_tempMid = scale(TB_y_tempMid, center = T, scale = F)) %>%
  dplyr::group_by(Group, Sex, condition, label) %>%
  dplyr::summarise(F1_tempMid = mean(F1_tempMid, na.rm = T),
                   F2_tempMid = mean(F2_tempMid, na.rm = T),
                   TB_x_tempMid = mean(TB_x_tempMid, na.rm = T),
                   TB_y_tempMid = mean(TB_y_tempMid, na.rm = T)) %>%
  dplyr::mutate(Sex = factor(Sex,
                             levels = c(
                               "M",
                               "F"
                             ),
                             labels = c(
                               "Male Speakers",
                               "Female Speakers"
                             )))
variability_xyCoords <- rio::import(file = "../Data/PreppedData/CollatedData/allSpeakers_tempMid.csv") %>%
  dplyr::select(DatabaseID, Group, condition, label,
                F1_tempMid, F2_tempMid,
                TB_x_tempMid, TB_y_tempMid) %>%
  base::merge(., speakers, no.dups = F) %>%
  dplyr::group_by(DatabaseID) %>%
  dplyr::mutate(TB_x_tempMid = scale(TB_x_tempMid, center = T, scale = F),
                TB_y_tempMid = scale(TB_y_tempMid, center = T, scale = F)) %>%
  tidyr::pivot_longer(cols = F1_tempMid:TB_y_tempMid,
                      names_to = "Dimension",
                      values_to = "Value") %>%
  dplyr::group_by(Group, Sex, condition, Dimension, label) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   SD = sd(Value, na.rm = T)) %>%
  dplyr::group_by(condition, Dimension) %>%
  dplyr::mutate(CV = abs(SD / M * 100),
                M_z = scale(M),
                SD_z = scale(SD))

coordVariability <- variability_xyCoords %>%
  ggplot() +
  aes(x = Dimension,
      y = SD_z) +
  geom_boxplot() +
  facet_wrap(~Sex)
coordVariability

aVSA <- vsaMeasures %>%
  dplyr::filter(condition == "conv") %>%
  ggplot() +
  aes(x = F2_tempMid,
      y = F1_tempMid,
      label = label,
      color = Group,
      linetype = Group,
      fill = Group) +
  geom_point() +
  geom_polygon(fill = NA) +
  geom_label(color = "white",
             show.legend = FALSE) +
  scale_x_reverse() +
  scale_y_reverse() +
  facet_grid(~ Sex) +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  
  # Labels
  labs(x = "F2",
       y = "F1",
       title = "Acoustic VSA") +
  
  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD))
aVSA

kVSA <- vsaMeasures %>%
  dplyr::filter(condition == "conv") %>%
  ggplot() +
  aes(x = TB_x_tempMid,
      y = TB_y_tempMid,
      label = label,
      color = Group,
      linetype = Group,
      fill = Group) +
  geom_point() +
  geom_polygon(
    fill=NA) +
  geom_label(color = "white",
             show.legend = FALSE) +
  scale_x_reverse() +
  facet_grid(~ Sex) +
  theme_minimal() +
  theme(aspect.ratio = 1) +
  
  # Labels
  labs(x = "Anterior-Posterior (x)",
       y = "Inferior-Superior (y)",
       title = "Kinematic VSA") +
  
  # Color Palate
  scale_color_manual(values = c(color_HC,color_PD)) +
  scale_fill_manual(values = c(color_HC,color_PD))
kVSA

vsaComparisons <- aVSA + kVSA + 
  patchwork::plot_layout(guides = "collect",
              ncol = 1)
vsaComparisons

ggsave(filename = "S1_vsaComparison.png",
       path = "Data/Plots/Results/",
       plot = vsaComparisons,
       height = 3.5,
       width = 3,
       units = "in",
       scale = 1.7)
```
