---
title: "Study 2: Tables"
---

This script generates the tables for Study 2 (Acoustic and kinematic predictors of intelligibility and articulatory precision in Parkinson’s disease).

# Packages
```{r}
library(tidyverse)
library(emmeans)
library(webshot2) # install.packages('webshot2')

# Making sure there is a Tables folder
dir.create(path = "Study-2/Tables", showWarnings = F)
```

## Table 2 - ICC values
```{r}
iccTable <- rio::import(file = "../Data/PreppedData/Reliability/ICC data.csv") %>%
  gt::gt() %>%
  gt::tab_spanner(columns = c("inter_ICC",
                              "inter_lbound",
                              "inter_ubound"),
                  label = "Inter-measurer") %>%
  gt::tab_spanner(columns = c("intra_ICC",
                              "intra_lbound",
                              "intra_ubound"),
                  label = "Intra-measurer")


gt::gtsave(data = iccTable,
           filename = "Tables/Table 2_Reliability.html")
```

## Table 3 - Point-Based Spatial Measures
```{r}
Int_PBS <-
  base::readRDS(file = "Models/Int_PBS.rds")
AP_PBS <-
  base::readRDS(file = "Models/AP_PBS.rds")

sjPlot::tab_model(
  Int_PBS,
  AP_PBS,
  dv.labels = c("Intelligibility", "Articulatory Precision"),
  file = "Tables/Table 3_Point-Based Spatial Measures Model Table.html"
)
```


## Table 4 - Transition-Based Spatial Measures
```{r}
Int_TBS <-
  base::readRDS(file = "Models/Int_TBS.rds")
AP_TBS <-
  base::readRDS(file = "Models/AP_TBS.rds")

sjPlot::tab_model(
  Int_TBS,
  AP_TBS,
  pred.labels = c("(Intercept)", "Kinematic Distance", "Sex [F]"),
  dv.labels = c("Intelligibility", "Articulatory Precision"),
  file = "Tables/Table 4_Transition-Based Spatial Measures Model Table.html"
)
```

## Table 5 - Spatiotemporal Measures
```{r}
Int_SpaTemp <-
  base::readRDS(file = "Models/Int_SpaTemp.rds")
AP_SpaTemp <-
  base::readRDS(file = "Models/AP_SpaTemp.rds")

sjPlot::tab_model(
  Int_SpaTemp,
  AP_SpaTemp,
  pred.labels = c("(Intercept)", "Sex [F]", "F2 Slope"),
  dv.labels = c("Intelligibility", "Articulatory Precision"),
  file = "Tables/Table 5_Spatiotemporal Measures Model Table.html"
)
```

# Supplemental Info
## Table S1 - HC Speaker Demo
```{r}
fileInventories <- rio::import("../Data/RawData/File Inventories.xlsx") %>%
  dplyr::select(DatabaseID = `Sub #`,
                Group,
                Sex,
                Age,
                dxTime = `Time Since Diagnosis`,
                MoCA)

listenerRatings <- rio::import(
  file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv"
) %>%
  dplyr::filter(condition == "conv") %>%
  dplyr::group_by(DatabaseID, StudyID) %>%
  dplyr::summarise(Rating_M = mean(Int_M, na.rm = T))

speakerList <-
  rio::import(file = "../Data/PreppedData/Speaker List_Clean.csv") %>%
  dplyr::select(!`Folder 2`:`Sentence Repetition`) %>%
  base::merge(., fileInventories) %>%
  base::merge(., listenerRatings) %>%
  
  # Making sure dxTime is numeric
  dplyr::mutate(dxTime = as.numeric(dxTime)) %>%
  
  # Refactoring Sex
  dplyr::mutate(Sex = factor(
    Sex,
    levels = c("M",
               "F"),
    labels = c("Male Speakers",
               "Female Speakers")
  )) %>%
  
  # Severity-surrogate ratings
  dplyr::mutate(
    Severity = case_when(
      Group == "HC" ~ "",
      Rating_M > 94 ~ "Normal",
      between(Rating_M, 85, 94.99) ~ "Mild",
      between(Rating_M, 70, 84.99) ~ "Moderate",
      between(Rating_M, 45, 69.99) ~ "Severe",
      Rating_M < 45 ~ "Profound"
    )
  ) %>%
  
  # Removing the MoCA Scores - Not all speakers had them
  dplyr::select(!MoCA)

# HC Speakers ----
speakerList %>%
  dplyr::filter(Group == "HC") %>%
  dplyr::select(!DatabaseID) %>%
  dplyr::arrange(StudyID) %>%
  
  # Creating the gt table
  gt::gt(rowname_col = "StudyID",
         groupname_col = "Sex") %>%
  
  # Title
  gt::tab_header(title = "Table S1",
                 subtitle = "Speaker demographics for the neurologically healthy control (HC) speaker group.") %>%
  
  # Replace missing values with blanks
  gt::sub_missing(columns = everything(),
                  rows = everything(),
                  missing_text = "") %>%
  
  # Renaming columns
  gt::cols_label(dxTime = "Time Since Diagnosis",
                 Rating_M = "Intelligibility (%)",) %>%
  
  # Formatting the Intelligibility data
  gt::fmt_number(columns = Rating_M,
                 decimals = 2,) %>%
  
  # Adding summary rows
  ## Male Speakers
  gt::summary_rows(
    groups = "Male Speakers",
    columns = c(Age, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list( ~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  ## Female Speakers
  gt::summary_rows(
    groups = "Female Speakers",
    columns = c(Age, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list( ~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  
  # Adding footnote to Intelligibility
  gt::tab_footnote(
    footnote = "The reported intelligibility (%) scores are aggregated from the Visual Analog Scale (VAS) ratings made for conversational speech samples in the current study.",
    locations = gt::cells_column_labels(columns = Rating_M)
  ) %>%
  
  # Adding footnote to HCM02
  gt::tab_footnote(
    footnote = "The HCM02 speaker, while healthy and intelligible, had a Spanish accent that likely influenced his intelligibility ratings. Further discussion about this speaker and the implications for his intelligibility ratings can be found in the limitations section.",
    locations = gt::cells_body(columns = Rating_M,
                               rows = StudyID == "HCM02")
  ) %>%
  
  # Adding footnote to HCM04
  gt::tab_footnote(
    footnote = "The HCM04 speaker, presented with a perceptually rough voice quality consistent with healthy aging. This voice quality likely influenced his intelligibility ratings.",
    locations = gt::cells_body(columns = Rating_M,
                               rows = StudyID == "HCM04")
  ) %>%
  
  # Format groups
  gt::tab_options(
    row_group.as_column = FALSE,
    table.font.size = 13,
    data_row.padding = 0
  ) %>%
  
  gt::cols_align(align = c("center"),
                 columns = StudyID:Severity) %>%
  
  # Hiding time since diagnosis and severity
  gt::cols_hide(columns = c(dxTime, Severity)) %>%
  
  # Saving the table
  gt::gtsave(filename = "Tables/Table S1_SpeakerDemo_HC.html")
```

## Table S2 - PD Speaker Demo
```{r}
# PD Speakers ----
speakerList %>%
  dplyr::filter(Group == "PD") %>%
  dplyr::select(!DatabaseID) %>%
  dplyr::arrange(StudyID) %>%
  
  # Creating the gt table
  gt::gt(rowname_col = "StudyID",
         groupname_col = "Sex") %>%
  
  # Title
  gt::tab_header(title = "Table S2",
                 subtitle = "Speaker demographics for the Parkinson’s (PD) speaker group.") %>%
  
  # Replace missing values with blanks
  gt::sub_missing(columns = everything(),
                  rows = everything(),
                  missing_text = "") %>%
  
  # Renaming columns
  gt::cols_label(dxTime = "Time Since Diagnosis (Years)",
                 Rating_M = "Intelligibility (%)",) %>%
  
  # Formatting the Intelligibility data
  gt::fmt_number(columns = Rating_M,
                 decimals = 2,) %>%
  
  # Formatting the dxTime data
  gt::fmt_number(columns = dxTime,
                 decimals = 0,) %>%
  
  # Adding summary rows
  ## Male Speakers
  gt::summary_rows(
    groups = "Male Speakers",
    columns = c(Age, dxTime, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list( ~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  ## Female Speakers
  gt::summary_rows(
    groups = "Female Speakers",
    columns = c(Age, dxTime, Rating_M),
    fns = list(
      M = ~ mean(., na.rm = TRUE),
      SD = ~ sd(., na.rm = TRUE)
    ),
    fmt = list( ~ gt::fmt_number(., decimals = 2))
  ) %>%
  
  # Adding footnote to Intelligibility
  gt::tab_footnote(
    footnote = "The reported intelligibility (%) scores are aggregated from the Visual Analog Scale (VAS) ratings made for conversational speech samples in the current study.",
    locations = gt::cells_column_labels(columns = Rating_M)
  ) %>%
  
  # Adding footnote to Severity
  gt::tab_footnote(
    footnote = "Severity labels were determined based on the intelligibility measures using the surrogate-severity measures outlined in Stipancic et al. (2022). Specifically, intelligibility values > 94% are `Normal`, 85% - 94% are `Mild`, 70% - 84% are `Moderate`, 45% - 69% are `Severe`, and < 45% are `Profound`.",
    locations = gt::cells_column_labels(columns = Severity)
  ) %>%
  
  # Format groups
  gt::tab_options(
    row_group.as_column = FALSE,
    table.font.size = 13,
    data_row.padding = 0
  ) %>%
  
  gt::cols_align(align = c("center"),
                 columns = StudyID:Severity) %>%
  
  # Saving the table
  gt::gtsave(filename = "Tables/Table S2_SpeakerDemo_PD.html")

```
## Table S3 - Descriptives Table
```{r}
# Perceptual Measures ----
perceptualMeasures <-
  rio::import(file = "../Data/PreppedData/ListenerData/ListenerRatings_allRatings.csv") %>%
  dplyr::select(!1) %>%
  
  # Selecting only the data we need
  dplyr::select(DatabaseID, Group, Sex, condition, ratingType, Rating)

## By Sex
perceptualMeasures_bySex <- perceptualMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, Sex, condition, ratingType) %>%
  dplyr::summarise(M = mean(Rating, na.rm = T),
                   SD = sd(Rating, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),)

## All Speakers
perceptualMeasures_allSpeakers <- perceptualMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, condition, ratingType) %>%
  dplyr::summarise(M = mean(Rating, na.rm = T),
                   SD = sd(Rating, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),) %>%
  
  # Add "All Speakers" label to the Sex
  dplyr::mutate(Sex = "All Speakers")


perceptualMeasures <- base::rbind(perceptualMeasures_allSpeakers,
                                  perceptualMeasures_bySex,
                                  deparse.level = 1) %>%
  dplyr::relocate(Sex, .before = ratingType) %>%
  dplyr::rename(Measure = ratingType)

# Removing the unneeded items
rm(perceptualMeasures_allSpeakers,
   perceptualMeasures_bySex)



# VSA Measures ----
vsaMeasures <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_vsaMeasures.csv") %>%
  
  # Converting aVSA from Hz to kHz, to make table cleaner
  dplyr::mutate(aVSA = aVSA / 1000) %>%
  
  # Selecting only the data we need
  dplyr::select(DatabaseID:kVSA) %>%
  
  # Formatting for the table
  tidyr::pivot_longer(cols = aVSA:kVSA,
                      names_to = "Measure",
                      values_to = "Value")

## By Sex
vsaMeasures_bySex <- vsaMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, Sex, condition, Measure) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   SD = sd(Value, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),)

## All Speakers
vsaMeasures_allSpeakers <- vsaMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, condition, Measure) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   SD = sd(Value, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),) %>%
  
  # Add "All Speakers" label to the Sex
  dplyr::mutate(Sex = "All Speakers")

vsaMeasures <- base::rbind(vsaMeasures_allSpeakers,
                           vsaMeasures_bySex,
                           deparse.level = 1) %>%
  dplyr::relocate(Sex, .before = Measure)

# Removing the unneeded items
rm(vsaMeasures_allSpeakers,
   vsaMeasures_bySex)

# /ai/ Measures ----
aiMeasures <-
  rio::import(file = "../Data/PreppedData/CollatedData/TargetMeasures_aiMeasures.csv") %>%
  
  # Selecting only the data we need
  dplyr::select(DatabaseID:Group,
                condition,
                acoDistance,
                kinDistance,
                F2_Slope,
                kinSpeed) %>%
  
  # Formatting for the table
  tidyr::pivot_longer(cols = acoDistance:kinSpeed,
                      names_to = "Measure",
                      values_to = "Value") %>%
  dplyr::filter(!is.na(Value))

## By sex
aiMeasures_bySex <- aiMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, Sex, condition, Measure) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   SD = sd(Value, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),)

## All Speakers
aiMeasures_allSpeakers <- aiMeasures %>%
  # Summarizing the measures by taking the average across groups
  dplyr::group_by(Group, condition, Measure) %>%
  dplyr::summarise(M = mean(Value, na.rm = T),
                   SD = sd(Value, na.rm = T),) %>%
  
  # Pivoting the data back to wide for the table
  tidyr::pivot_wider(names_from = c(Group, condition),
                     values_from = c(M, SD),) %>%
  
  # Add "All Speakers" label to the Sex
  dplyr::mutate(Sex = "All Speakers")

aiMeasures <- base::rbind(aiMeasures_allSpeakers,
                          aiMeasures_bySex,
                          deparse.level = 1) %>%
  dplyr::relocate(Sex, .before = Measure)


# Removing the unneeded items
rm(aiMeasures_allSpeakers,
   aiMeasures_bySex)


# All Measures ----
descriptivesData <- base::rbind(perceptualMeasures,
                                vsaMeasures,
                                aiMeasures,
                                deparse.level = 1) %>%
  dplyr::mutate_at(vars(-c(Sex, Measure)), round, digits = 2) %>%
  dplyr::mutate(
    Measure = factor(
      Measure,
      levels = c(
        "Int",
        "AP",
        "aVSA",
        "acoDistance",
        "F2_Slope",
        "kVSA",
        "kinDistance",
        "kinSpeed"
      ),
      labels = c(
        "Intelligibility (VAS)",
        "Articulatory Precision (VAS)",
        "Acoustic VSA (kHz\U00B2)",
        "Acoustic Distance (Hz)",
        "F2 Slope (Hz/ms)",
        "Kinematic VSA (mm\U00B2)",
        "Kinematic Distance (mm)",
        "Kinematic Speed (mm/s)"
      )
    ),
    Sex = factor(
      Sex,
      levels = c("All Speakers",
                 "M",
                 "F"),
      labels = c("All Speakers",
                 "Male Speakers",
                 "Female Speakers")
    )
  ) %>%
  dplyr::arrange(Measure) %>%
  dplyr::select(
    Sex,
    Measure,
    M_HC_conv,
    SD_HC_conv,
    M_PD_conv,
    SD_PD_conv,
    M_HC_lessClear,
    SD_HC_lessClear,
    M_PD_lessClear,
    SD_PD_lessClear,
    M_HC_moreClear,
    SD_HC_moreClear,
    M_PD_moreClear,
    SD_PD_moreClear,
  )

# Creating the GT table
descriptivesTable <- descriptivesData %>%
  gt::gt(rowname_col = "Measure",
         groupname_col = "Sex") %>%
  # Title
  #gt::tab_header(title = "Table S3",
  #               subtitle = "The target measures across the speaking conditions, presented for male, female, and all speakers.") %>%
  
  
  # Spanner 1: PD Speakers
  gt::tab_spanner(
    label = "PD",
    level = 1,
    gather = FALSE,
    columns = c(
      M_PD_conv,
      SD_PD_conv,
      M_PD_lessClear,
      SD_PD_lessClear,
      M_PD_moreClear,
      SD_PD_moreClear
    )
  ) %>%
  # Spanner 1: HC Speakers
  gt::tab_spanner(
    label = "HC",
    level = 1,
    gather = FALSE,
    columns = c(
      M_HC_conv,
      SD_HC_conv,
      M_HC_lessClear,
      SD_HC_lessClear,
      M_HC_moreClear,
      SD_HC_moreClear
    )
  ) %>%
  # Spanner 2: Conversational
  gt::tab_spanner(
    label = "Conversational",
    level = 2,
    gather = TRUE,
    columns = c(M_HC_conv,
                SD_HC_conv,
                M_PD_conv,
                SD_PD_conv)
  ) %>%
  # Spanner 2: Less Clear
  gt::tab_spanner(
    label = "Less Clear",
    level = 2,
    gather = TRUE,
    columns = c(
      M_HC_lessClear,
      SD_HC_lessClear,
      M_PD_lessClear,
      SD_PD_lessClear
    )
  ) %>%
  # Spanner 2: More Clear
  gt::tab_spanner(
    label = "More Clear",
    level = 2,
    gather = TRUE,
    columns = c(
      M_HC_moreClear,
      SD_HC_moreClear,
      M_PD_moreClear,
      SD_PD_moreClear
    )
  ) %>%
  gt::cols_label(
    M_HC_conv = "M",
    SD_HC_conv = "SD",
    M_PD_conv = "M",
    SD_PD_conv = "SD",
    M_HC_lessClear = "M",
    SD_HC_lessClear = "SD",
    M_PD_lessClear = "M",
    SD_PD_lessClear = "SD",
    M_HC_moreClear = "M",
    SD_HC_moreClear = "SD",
    M_PD_moreClear = "M",
    SD_PD_moreClear = "SD"
  ) %>%
  
  # Align the measure labels to the right
  gt::cols_align(align = c("right"),
                 columns = Measure) %>%
  
  # Format groups
  gt::tab_options(
    row_group.as_column = FALSE,
    table.font.size = 10,
    column_labels.padding = 0,
    data_row.padding = 5,
    page.orientation = "landscape",
    page.width = "11in",
    page.height = "8.5in"
  )

# Save as .pdf
gt::gtsave(data = descriptivesTable,
           filename = "Tables/Table S3_descriptivesTable.html")


```
## Table S4 - Int ~ Point-Based Spatial Measures Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/Int_PBS_m1.rds"),
  base::readRDS(file = "Models/Int_PBS.rds"),
  dv.labels = c("Model 1", "Final Model"),
  show.ci = F,
  file = "Tables/Table S4_Int PBS Model.html"
)
```


## Table S5 - Int ~ Transition-Based Spatial Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/Int_TBS_m1.rds"),
  base::readRDS(file = "Models/Int_TBS.rds"),
  dv.labels = c("Model 1", "Final Model"),
  show.ci = F,
  file = "Tables/Table S5_Int TBS Model.html"
)
```

## Table S6 - Int ~ Spatiotemporal Measure Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/Int_SpaTemp_m1.rds"),
  base::readRDS(file = "Models/Int_SpaTemp_m2.rds"),
  base::readRDS(file = "Models/Int_SpaTemp.rds"),
  dv.labels = c("Model 1", "Model 2", "Final Model"),
  show.ci = F,
  p.threshold = c(0.008333333, 0.008333333, 0.008333333),
 p.style = c("numeric"),
  file = "Tables/Table S6_Int Spatiotemporal Model.html"
)
```

## Table S7 - AP ~ Point-Based Spatial Measures Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/AP_PBS_m1.rds"),
  base::readRDS(file = "Models/AP_PBS.rds"),
  dv.labels = c("Model 1", "Final Model"),
  show.ci = F,
  file = "Tables/Table S7_AP PBS Model.html"
)
```

## Table S8 - AP ~ Transition-Based Spatial Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/AP_TBS_m1.rds"),
  base::readRDS(file = "Models/AP_TBS.rds"),
  dv.labels = c("Model 1", "Final Model"),
  show.ci = F,
  file = "Tables/Table S8_AP TBS Model.html"
)
```

## Table S9 - AP ~ Spatiotemporal Measure Model Building
```{r}
sjPlot::tab_model(
  base::readRDS(file = "Models/AP_SpaTemp_m1.rds"),
  base::readRDS(file = "Models/AP_SpaTemp_m2.rds"),
  base::readRDS(file = "Models/AP_SpaTemp.rds"),
  dv.labels = c("Model 1", "Model 2", "Final Model"),
  show.ci = F,
  file = "Tables/Table S9_AP Spatiotemporal Measure Model.html"
)
```
